---
title: "integrated_analyses"
author: "Alex Brown"
date: "2025-10-30"
output: html_document
---



# Load packages

```{r, include=FALSE}
library(Seurat)
library(SeuratWrappers)
library(tidyverse)
library(Biobase)
library(BiocGenerics)
library(ggplot2)
library(gridExtra)
library(harmony)
library(AnnotationDbi)
library(org.Mm.eg.db)
library(msigdbr)
library(clusterProfiler)
library(monocle3)
library(NMF)
library(circlize)
library(ComplexHeatmap)
library(CellChat)
```



# Load data

```{r, include=FALSE}
load("sc_combined_subclusters.RData", verbose = TRUE)
```



# Experiments

```{r}
unique(sc_combined$experiment)
```



# Samples

```{r}
unique(sc_combined$orig.ident)
```



# Clusters

```{r}
unique(sc_combined$seurat_clusters)
```



# Subclusters

```{r}
unique(sc_combined$subcluster)
```



# UMAPs

## UMAP by cluster, subcluster, sample, or experiment

```{r}
DimPlot(sc_combined, reduction = "umap", group.by = "#seurat_cluster OR subcluster OR orig.ident OR experiment", repel = TRUE, pt.size = 1) +
  ggplot2::labs(title = "", x = "UMAP1", y = "UMAP2") +
  theme(axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank())
```

### UMAP by cluster/subcluster/sample/experiment, only including certain ones. NOTE - this will also allow you to colour by cluster OR sample OR experiment, so you can get different combinations (i.e. all/certain experiments highlighted by sample, all/certain clusters highlighted by sample, etc.)

```{r}
DimPlot(
  subset(sc_combined, subset = #seurat_clusters OR subcluster OR orig.ident OR experiment %in% c("#name_1", "#name_2", "#etc.")),
  reduction = "umap",
  group.by = "#seurat_clusters OR subcluster OR orig.ident OR experiment", # THIS IS WHAT CELLS WILL BE COLOURED BY
  repel = TRUE,
  pt.size = 1,
  cols = c(
    "#name_1" = "#colour_1",
    "#name_2"       = "#colour_2",
    "#etc." # NAMES SHOULD MATCH THE group.by FUNCTION. REMOVE cols FUNCTION IF YOU DO NOT WANT TO HIGHLIGHT CERTAIN FEATURES
  )
) +
  ggplot2::labs(title = "", x = "UMAP1", y = "UMAP2") +
  theme(
    axis.text.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks = element_blank()
  )
```

### NOTE - When each plot is generated, include a meta table to include the experiments, samples, clusters, and subclusters included in the analysis, and how many cells are from each. Off to the side, not a part of the plot itself.

```{r}
table(sc_combined$experiment) # per experiment
table(sc_combined$orig.ident) # per sample
table(sc_combined$seurat_clusters) # per cluster
table(sc_combined$subcluster) # per subcluster
```



# Dotplots

## DotPlot to distinguish clusters

```{r}
DefaultAssay(sc_combined) <- "RNA"
Idents(sc_combined) <- "seurat_clusters"

DotPlot(object = sc_combined, features = c(
  "Pax7", "Myf5", # MuSCs
  "Myod1", "Myog", # Myoblast
  "Acta1", # Myonuclei 
    "Myh7", ## TI 
    "Myh2", ## TIIa 
    "Myh4", ## TIIb 
    "Myh1", ## TIIx
  "Cdh5", "Pecam1", # Endothelial cells 
    "Ly6a", "Fbln5", ## large artery
    "Lrg1", "Icam1", ## large vein
    "Fmo1", "Fmo2", ## capillary venous
    "Apln", ## angiogenic
  "Myl9", "Pdgfrb", ## vSMCs/pericytes
  "Pdgfra", # FAPs
    "Cd34", "Dpp4", "Pi16", ## stem FAPs
    "Mme", "Mmp2", "Col3a1", ## pro-remodeling
    "Dlk1", "Tenm2",
    "Dcn", ## fibroblast
  "Tnmd", # Tenocytes
  "Ptprc", # Immune
    "Mmrn1", "Ccl21a", ## platelet
    "Cpa3", "Tpsb2", ## mast cells
    "Fscn1", "Flt3", "Cd209a", ## dendritic cells
    "Itgam", "Ccr2", "Fabp5", "Cx3cr1", "Ly6c1", "Ly6c2", ## monocytes
      "Cd68", "Cd74", "Cd83", ### macrophages
      "Ccl6", "Ccl9", #### pro-inflammatory macrophage
      "C1qa", #### anti-inflammatory macrophage
    "S100a8", "S100a9", ## neutrophils
    "Ms4a1", "Cd79a", # B cell
    "Il7r", "Cd4", "Cd8a", "Cd27",  # T cell
    "Nkg7", "Klra7", # NK cell
  "Ptn", "Cdh19", "Mpz", "S100b", ### Neural/glial/Schwann cells
  "Gypa", "Hba-a2", ### Erythrocytes
  "Krt15", "Epcam" ### Epithelial cells
  )) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, face = "italic")) +
  scale_color_gradientn(colors = c("red", "white", "blue")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "italic"))
```


## Dotplot between clusters/subclusters

```{r}
DefaultAssay(sc_combined) <- "RNA"
Idents(sc_combined) <- "#seurat_clusters OR subcluster"

DotPlot(object = sc_combined, idents = c("#list seurat_clusters OR subcluster names here"), features = c("#list gene names here"
  )) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, face = "italic")) +
  scale_color_gradientn(colors = c("red", "white", "blue")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "italic"))
```


## DotPlot between conditions

```{r}
DefaultAssay(sc_combined) <- "RNA"
Idents(sc_combined) <- "orig.ident"

DotPlot(object = sc_combined, idents = c("#list sample names here"), features = c("#list gene names here" 
  )) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, face = "italic")) +
  scale_color_gradientn(colors = c("red", "white", "blue")) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, face = "italic"))
```



# Differential gene expression values

## Before visualizing gene expression differences between clusters, subclusters, and samples, we need to specify which cells to include in the analysis. Have check box of experiment with sub-boxes for sample, additional boxes for clusters with sub-boxes for subcluster.

```{r, include=FALSE}
sc_subset <- subset(
  sc_combined,
  subset = experiment %in% c("#experiment_1", "#experiment_2", "#etc.") &
           orig.ident %in% c("#orig.ident_1", "#orig.ident_2", "#etc.") &
           seurat_clusters %in% c("#seurat_cluster_1", "#seurat_cluster_2", "#etc.") &
           subcluster %in% c("#subcluster_1", "#subcluster_2", "etc.")
)
```


## Output a table that summarises all of the experiments/samples/clusters/subclusters included in the analyses, and the number of cells associated with each

```{r}
meta_table <- sc_subset@meta.data %>%
  group_by(experiment, orig.ident, seurat_clusters, subcluster) %>%
  summarise(n_cells = n(), .groups = "drop") %>%
  arrange(experiment, orig.ident, seurat_clusters, subcluster)

view(meta_table)

### Option to download table
write.csv(meta_table, file = "meta_table.csv", row.names = FALSE)
```

### After choosing which cells to include, have options to do differential gene expression analysis, which will return a spreadsheet of all of the differentially expressed genes in the specified conditions.


## Get DEGs

```{r, include=FALSE}
Idents(sc_subset) <- "#experiment OR orig.ident OR seurat_clusters OR subcluster"

DEGs <- FindMarkers(sc_subset, ident.1 = c("#name_comparison_1", "#name_comparison_2", "#etc."), ident.2 = c("#name_reference_1", "#name_reference_2", "#etc."), logfc.threshold = 0, min.pct = 0.10, verbose = FALSE)
### EXAMPLE - if we wanted to get DEGs for satellite cells in LLC and C26 models compared to controls. Subset for Satellite cells cluster (during subset step). Set IDENTS as "orig.ident". Then #name_comparison_1 = Agca_snLLC_LLC, #name_comparison_2 = Brown_scLLC_3.5w, #name_comparison_3 = Pryce_scC26_C26; #name_reference_1 = Agca_snLLC_CTL, #name_reference_2 = Brown_scLLC_CTL, #name_reference_3 = Pryce_scC26_CTL.

### HAVE OPTION TO SPECIFY p_val_adj AND avg_log2FC CUTOFFS
DEGs <- rownames(subset(
  na.omit(DEGs), 
  p_val_adj < 0.05 & (avg_log2FC > 0.2 | avg_log2FC < -0.2)
))

### View DEGs on website
view(DEGs)

### Download DEGs spreadsheet
write.csv(DEGs, file = "DEGs.csv")
```


## GO terms and KEGG pathway analysis

```{r, include=FALSE}
DEGs_up <- rownames(DEGs[DEGs$avg_log2FC > 0,])

DEGs_down <- rownames(DEGs_cachectic_MuSCs[DEGs_cachectic_MuSCs$avg_log2FC < 0,])
```

### GO terms

```{r, include=FALSE}
DEGs_upgo <- enrichGO(gene = DEGs_up, OrgDb = "org.Mm.eg.db", keyType = "SYMBOL", ont = "BP")
DEGs_downgo <- enrichGO(gene = DEGs_down, OrgDb = "org.Mm.eg.db", keyType = "SYMBOL", ont = "BP")

### View GO terms on website
view(DEGs_upgo)
view(DEGs_downgo)

### Download GO terms spreadsheet
write.csv(DEGs_upgo, file = "DEGs_upgo.csv", row.names = FALSE)
write.csv(DEGs_downgo, file = "DEGs_downgo.csv", row.names = FALSE)
```

### Plot GO terms

```{r}
# UP
up_terms <- c(#List of row numbers from DEGs_upgo for the terms that you want to plot. Is there a way to make a checklist of the enriched terms that come up so that they can pick and choose which terms to plot?)
go_up <- DEGs_upgo[up_terms, ]

go_up$Description <- gsub(" - Mus musculus \\(house mouse\\)$", "", go_up$Description)

ggplot(go_up, aes(x = FoldEnrichment, 
                           y = reorder(Description, FoldEnrichment),
                           size = Count, 
                           color = p.adjust)) +
  geom_point() +
  scale_color_gradient(low = "blue", high = "red", name = "adj. p-value") +
  labs(x = "Fold Enrichment", y = NULL, 
       title = "#CHOOSE TITLE NAME") +
  theme_minimal() +
  theme(
    axis.line = element_line(color = "black"),
    axis.ticks = element_line(color = "black")
  )



# DOWN
down_terms <- c(#List of row numbers from DEGs_downgo for the terms that you want to plot. Is there a way to make a checklist of the enriched terms that come up so that they can pick and choose which terms to plot?)
go_down <- DEGs_downgo[down_terms, ]

go_down$Description <- gsub(" - Mus musculus \\(house mouse\\)$", "", go_down$Description)

ggplot(go_down, aes(x = FoldEnrichment, 
                           y = reorder(Description, FoldEnrichment),
                           size = Count, 
                           color = p.adjust)) +
  geom_point() +
  scale_color_gradient(low = "blue", high = "red", name = "adj. p-value") +
  labs(x = "Fold Enrichment", y = NULL, 
       title = "#CHOOSE TITLE NAME") +
  theme_minimal() +
  theme(
    axis.line = element_line(color = "black"),
    axis.ticks = element_line(color = "black")
  )

### NOTE - For specifying FoldEnrichment, Count, p.adjust, I want these as the default setting. Is there a way to pick and choose which values you want to customize? Where I specified these values, I would like the option of specifying GeneRatio, BgRatio, RichFactor, FoldEnrichment, zScore, pvalue, p.adjust, qvalue, Count. Then the labels would need to adjust accordingly.
```


### KEGG pathways

```{r, include=FALSE}
DEGs_upIDs <- bitr(DEGs_up,
                  fromType = "SYMBOL",
                  toType   = "ENTREZID",
                  OrgDb    = org.Mm.eg.db)

DEGs_upkegg <- enrichKEGG(
  gene         = DEGs_upIDs$ENTREZID,
  organism     = "mmu",
  keyType      = "kegg",
  pvalueCutoff = 0.05)
### Specify pvalueCutoff

DEGs_downIDs <- bitr(DEGs_down,
                  fromType = "SYMBOL",
                  toType   = "ENTREZID",
                  OrgDb    = org.Mm.eg.db)

DEGs_downkegg <- enrichKEGG(
  gene         = DEGs_downIDs$ENTREZID,
  organism     = "mmu",
  keyType      = "kegg",
  pvalueCutoff = 0.05)
### Specify pvalueCutoff

### View enriched KEGG pathways on website
view(DEGs_upkegg)
view(DEGs_downkegg)

### Download enriched KEGG pathways spreadsheet
write.csv(DEGs_upkegg, file = "DEGs_upkegg.csv", row.names = FALSE)
write.csv(DEGs_downkegg, file = "DEGs_downkegg.csv", row.names = FALSE)
```

### Plot KEGG pathways

```{r}
# UP

signaling_pathways_up <- c(#List of row numbers from DEGs_upkegg for the terms that you want to plot. Is there a way to make a checklist of the enriched terms that come up so that they can pick and choose which terms to plot?)
kegg_signaling_up <- DEGs_upkegg[signaling_pathways_up, ]

kegg_signaling_up$Description <- gsub(" - Mus musculus \\(house mouse\\)$", "", kegg_signaling_up$Description)

ggplot(kegg_signaling_up, aes(x = FoldEnrichment, 
                           y = reorder(Description, FoldEnrichment),
                           size = Count, 
                           color = p.adjust)) +
  geom_point() +
  scale_color_gradient(low = "blue", high = "red", name = "adj. p-value") +
  labs(x = "Fold Enrichment", y = NULL, 
       title = "#CHOOSE TITLE NAME") +
  theme_minimal() +
  theme(
    axis.line = element_line(color = "black"),
    axis.ticks = element_line(color = "black")
  )



# DOWN

signaling_pathways_down <- c(#List of row numbers from DEGs_downkegg for the terms that you want to plot. Is there a way to make a checklist of the enriched terms that come up so that they can pick and choose which terms to plot?)
kegg_signaling_down <- DEGs_downkegg[signaling_pathways_down, ]

kegg_signaling_down$Description <- gsub(" - Mus musculus \\(house mouse\\)$", "", kegg_signaling_down$Description)

ggplot(kegg_signaling_down, aes(x = FoldEnrichment, 
                           y = reorder(Description, FoldEnrichment),
                           size = Count, 
                           color = p.adjust)) +
  geom_point() +
  scale_color_gradient(low = "blue", high = "red", name = "adj. p-value") +
  labs(x = "Fold Enrichment", y = NULL, 
       title = "#CHOOSE TITLE NAME") +
  theme_minimal() +
  theme(
    axis.line = element_line(color = "black"),
    axis.ticks = element_line(color = "black")
  )

### NOTE - For specifying FoldEnrichment, Count, p.adjust, I want these as the default setting. Is there a way to pick and choose which values you want to customize? Where I specified these values, I would like the option of specifying GeneRatio, BgRatio, RichFactor, FoldEnrichment, zScore, pvalue, p.adjust, qvalue, Count. Then the labels would need to adjust accordingly.
```

### Next, have options to make violin/box plots split by clusters, subclusters, or samples (see below) for specific genes. Since they only generate one gene at a time, have an option to generate additional plots using the same subset settings (specified above), split by a different characteristic, or go back to subset settings.


## Violin plots of DEGs between clusters (ex. SCs vs. Myoblasts vs. Myonuclei vs. ECs, etc.)

```{r}
Idents(sc_subset) <- "seurat_clusters"

VlnPlot(subset(sc_subset, subset = seurat_clusters %in% c("#cluster_name_1", "#cluster_name_2", "#etc.")), 
        features = "#gene_name",
        pt.size = 0,
        cols = c("#cluster_name_1" = "#colour_1", "#cluster_name_2" = "#colour_2", "#etc.")) + # LEAVE BLANK FOR DEFAULT COLOURS
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    plot.title = element_text(face = "italic")
  ) +
  labs(x = NULL, y = "Expression", title = expression(italic("#gene_name")))

AverageExpression(sc_subset, features = "#gene_name")$RNA["#gene_name", ]
```



## Violin plots of DEGs between subclusters (ex. Quiescent SCs vs. Activated SCs vs. Cachectic SCs, etc.). AverageExperssion (bottom) to get expression value numbers.

```{r}
Idents(sc_subset) <- "subcluster"

VlnPlot(subset(sc_subset, subset = subcluster %in% c("#subcluster_name_1", "#subcluster_name_2", "#etc.")), 
        features = "#gene_name",
        pt.size = 0,
        cols = c("#subcluster_name_1" = "#colour_1", "#subcluster_name_2" = "#colour_2", "#etc.")) + # LEAVE BLANK FOR DEFAULT COLOURS
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    plot.title = element_text(face = "italic")
  ) +
  labs(x = NULL, y = "Expression", title = expression(italic("#gene_name")))

AverageExpression(sc_subset, features = "#gene_name")$RNA["#gene_name", ]
```


## Violin plots of DEGs between samples (ex. Brown_scLLC_CTL vs. Brown_scLLC_2w vs. Brown_scLLC_2.5w vs. Brown_scLLC_3.5w)

```{r}
Idents(sc_subset) <- "orig.ident"

VlnPlot(subset(sc_subset, subset = orig.ident %in% c("#sample_name_1", "#sample_name_2", "#etc.")), 
        features = "#gene_name",
        pt.size = 0,
        cols = c("#sample_name_1" = "#colour_1", "#sample_name_2" = "#colour_2", "#etc.")) + # LEAVE BLANK FOR DEFAULT COLOURS
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    plot.title = element_text(face = "italic")
  ) +
  labs(x = NULL, y = "Expression", title = expression(italic("#gene_name")))

AverageExpression(sc_subset, features = "#gene_name")$RNA["#gene_name", ]
```


## Boxplots of DEGs between clusters (ex. SCs vs. Myoblasts vs. Myonuclei vs. ECs, etc.)

```{r}
Idents(sc_subset) <- "seurat_clusters"

ggplot(FetchData(
  subset(sc_subset, idents = c("#cluster_name_1", "#cluster_name_2", "#etc.")),
  vars = c("#gene_name", "seurat_clusters")
), aes(x = seurat_clusters, y = !!sym("#gene_name"), fill = seurat_clusters)) +
  geom_boxplot(outlier.shape = NA, width = 0.6) +
  scale_fill_manual(values = c(
    "#cluster_name_1" = "#colour_1",
    "#cluster_name_2" = "#colour_2"
    # Leave blank for default colors
  )) +
  theme_classic() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "italic")
  ) +
  labs(
    x = NULL,
    y = "Expression",
    title = expression(italic("#gene_name"))
  )

AverageExpression(sc_subset, features = "#gene_name")$RNA["#gene_name", ]
```


## Boxplots of DEGs between subclusters (ex. Quiescent SCs vs. Activated SCs vs. Cachectic SCs, etc.)

```{r}
Idents(sc_subset) <- "subcluster"

ggplot(FetchData(
  subset(sc_subset, idents = c("#subcluster_name_1", "#subcluster_name_2", "#etc.")),
  vars = c("#gene_name", "subcluster")
), aes(x = subcluster, y = !!sym("#gene_name"), fill = subcluster)) +
  geom_boxplot(outlier.shape = NA, width = 0.6) +
  scale_fill_manual(values = c(
    "#subcluster_name_1" = "#colour_1",
    "#subcluster_name_2" = "#colour_2"
    # Leave blank for default colors
  )) +
  theme_classic() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "italic")
  ) +
  labs(
    x = NULL,
    y = "Expression",
    title = expression(italic("#gene_name"))
  )

AverageExpression(sc_subset, features = "#gene_name")$RNA["#gene_name", ]
```


## Boxplots of DEGs between samples (ex. Brown_scLLC_CTL vs. Brown_scLLC_2w vs. Brown_scLLC_2.5w vs. Brown_scLLC_3.5w)

```{r}
Idents(sc_subset) <- "orig.ident"

ggplot(FetchData(
  subset(sc_subset, idents = c("#sample_name_1", "#sample_name_2", "#etc.")),
  vars = c("#gene_name", "orig.ident")
), aes(x = orig.ident, y = !!sym("#gene_name"), fill = orig.ident)) +
  geom_boxplot(outlier.shape = NA, width = 0.6) +
  scale_fill_manual(values = c(
    "#sample_name_1" = "#colour_1",
    "#sample_name_2" = "#colour_2"
    # Leave blank for default colors
  )) +
  theme_classic() +
  theme(
    legend.position = "none",
    axis.text.x = element_text(angle = 45, vjust = 1, hjust = 1),
    plot.title = element_text(hjust = 0.5, face = "italic")
  ) +
  labs(
    x = NULL,
    y = "Expression",
    title = expression(italic("#gene_name"))
  )

AverageExpression(sc_subset, features = "#gene_name")$RNA["#gene_name", ]
```

### SAVE PLOTS. Have the option to save each plot as png, jpeg, tiff, bmp, svg, eps, pdf formats, specify width (default = 6), height (default = 4), units (default = "in"), res (default = 600). Have AverageExpression values come up alongside the plots so people can see them and save them if they want. 



# Pseudotime

## Before visualizing cells in pseudotime, we need to again specify which cells to include in the analysis. Have check box of experiment with sub-boxes for sample, additional boxes for clusters with sub-boxes for subcluster.

```{r, include=FALSE}
sc_subset <- subset(
  sc_combined,
  subset = experiment %in% c("#experiment_1", "#experiment_2", "#etc.") &
           orig.ident %in% c("#orig.ident_1", "#orig.ident_2", "#etc.") &
           seurat_clusters %in% c("#seurat_cluster_1", "#seurat_cluster_2", "#etc.") &
           subcluster %in% c("#subcluster_1", "#subcluster_2", "etc.")
)
```


## Output a table that summarises all of the experiments/samples/clusters/subclusters included in the analyses, and the number of cells associated with each

```{r}
meta_table <- sc_subset@meta.data %>%
  group_by(experiment, orig.ident, seurat_clusters, subcluster) %>%
  summarise(n_cells = n(), .groups = "drop") %>%
  arrange(experiment, orig.ident, seurat_clusters)

view(meta_table)

### Option to download table
write.csv(meta_table, file = "meta_table.csv", row.names = FALSE)
```


## Convert sc_combined to cell_data_set

```{r, include=FALSE}
Idents(sc_subset) <- "subcluster"

sc_subset_cds <- as.cell_data_set(sc_subset)
fData(sc_subset_cds)$gene_short_name <- rownames(fData(sc_subset_cds))
```


## Assign partitions

```{r, include=FALSE}
recreate.partition <- c(rep(1, length(sc_subset_cds@colData@rownames)))
names(recreate.partition) <- sc_subset_cds@colData@rownames
recreate.partition <- as.factor(recreate.partition)

sc_subset_cds@clusters$UMAP$partitions <- recreate.partition
```


## Assign cluster information

```{r, include=FALSE}
list_sc_subset_clusters <- sc_subset@active.ident
sc_subset_cds@clusters$UMAP$clusters <- list_sc_subset_clusters
```


## Assign UMAP coordinate - cell embedding

```{r, include=FALSE}
sc_subset_cds@int_colData@listData$reducedDims$UMAP <- sc_subset@reductions$umap@cell.embeddings
```


## Order cells in pseudotime

```{r, include=FALSE}
sc_subset_cds <- learn_graph(sc_subset_cds, use_partition = FALSE)

cluster_assignments <- sc_subset_cds@clusters$UMAP$clusters

root_cells <- names(cluster_assignments[cluster_assignments == "#name_root_subcluster"])

sc_subset_cds <- order_cells(sc_subset_cds, reduction_method = "UMAP", root_cells = root_cells)
```


## Add pseudotime to metadata

```{r, include=FALSE}
sc_subset_cds$monocle3_pseudotime <- pseudotime(sc_subset_cds)
```


## Plot in pseudotime

```{r}
plot_cells(sc_subset_cds, color_cells_by = "pseudotime", 
           label_branch_points = FALSE, 
           label_roots = FALSE,
           label_leaves = FALSE,
           group_label_size = 3,
           cell_size = 1.5,
           trajectory_graph_color = "green") +
  theme(axis.text.x = element_blank(), axis.text.y = element_blank(), axis.ticks = element_blank())

### Have options to specify labeling branch points, roots, leaves, and trajectory colour.
```


## Check pseudotime values by clusters ("check" to see that the early cells are indeed at a lower pseudotime than the later differentiated)

```{r}
sc_subset_pseudotime_data <- as.data.frame(colData(sc_subset_cds))

ggplot(sc_subset_pseudotime_data, aes(x = subcluster, y = monocle3_pseudotime, fill = subcluster)) +
  geom_boxplot(show.legend = FALSE, outlier.shape = NA) +
  labs(x = NULL, y = "Pseudotime") +
  scale_fill_manual(values = c(
    "#subcluster_1" = "#colour_1",
    "#subcluster_2" = "#colour_2",
    "#etc." = "#etc."
  )) +
  theme_classic() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1)
  )
```
