---
title: "integrated_cellchat"
author: "Alex Brown"
date: "2025-11-04"
output: html_document
---




# Load packages

```{r, include=FALSE}
library(Seurat)
library(SeuratWrappers)
library(tidyverse)
library(Biobase)
library(BiocGenerics)
library(ggplot2)
library(gridExtra)
library(harmony)
library(AnnotationDbi)
library(org.Mm.eg.db)
library(msigdbr)
library(clusterProfiler)
library(monocle3)
library(NMF)
library(circlize)
library(ComplexHeatmap)
library(CellChat)
```



# Load data

```{r, include=FALSE}
load("sc_combined_subclusters.RData")
```



# Remove unecessary objects to improve processing

```{r, include=FALSE}
rm(DEGs_sc_combined, sc_combined)
```



# CellChat

## Create CellChat object

```{r, include=FALSE}
data_input_Agca_snLLC_CTL <- GetAssayData(Agca_snLLC_CTL, assay = "RNA", layer = "data")
data_input_Agca_snLLC_LLC <- GetAssayData(Agca_snLLC_LLC, assay = "RNA", layer = "data")
data_input_Brown_scLLC_CTL <- GetAssayData(Brown_scLLC_CTL, assay = "RNA", layer = "data")
data_input_Brown_scLLC_2w <- GetAssayData(Brown_scLLC_2w, assay = "RNA", layer = "data")
data_input_Brown_scLLC_2.5w <- GetAssayData(Brown_scLLC_2.5w, assay = "RNA", layer = "data")
data_input_Brown_scLLC_3.5w <- GetAssayData(Brown_scLLC_3.5w, assay = "RNA", layer = "data")
data_input_Kim_scB16F10_CTL <- GetAssayData(Kim_scB16F10_CTL, assay = "RNA", layer = "data")
data_input_Kim_scB16F10_B16F10 <- GetAssayData(Kim_scB16F10_B16F10, assay = "RNA", layer = "data")
data_input_Pryce_scC26_CTL <- GetAssayData(Pryce_scC26_CTL, assay = "RNA", layer = "data")
data_input_Pryce_scC26_C26 <- GetAssayData(Pryce_scC26_C26, assay = "RNA", layer = "data")
data_input_Pryce_scKPP_CTL <- GetAssayData(Pryce_scKPP_CTL, assay = "RNA", layer = "data")
data_input_Pryce_scKPP_KPP <- GetAssayData(Pryce_scKPP_KPP, assay = "RNA", layer = "data")
data_input_Zhang_snKIC_CTL <- GetAssayData(Zhang_snKIC_CTL, assay = "RNA", layer = "data")
data_input_Zhang_snKIC_KIC <- GetAssayData(Zhang_snKIC_KIC, assay = "RNA", layer = "data")

# === Metadata ===
labels_Agca_snLLC_CTL <- Agca_snLLC_CTL@meta.data$seurat_clusters
samples_Agca_snLLC_CTL <- Agca_snLLC_CTL@meta.data$orig.ident
labels_Agca_snLLC_LLC <- Agca_snLLC_LLC@meta.data$seurat_clusters
samples_Agca_snLLC_LLC <- Agca_snLLC_LLC@meta.data$orig.ident
labels_Brown_scLLC_CTL <- Brown_scLLC_CTL@meta.data$seurat_clusters
samples_Brown_scLLC_CTL <- Brown_scLLC_CTL@meta.data$orig.ident
labels_Brown_scLLC_2w <- Brown_scLLC_2w@meta.data$seurat_clusters
samples_Brown_scLLC_2w <- Brown_scLLC_2w@meta.data$orig.ident
labels_Brown_scLLC_2.5w <- Brown_scLLC_2.5w@meta.data$seurat_clusters
samples_Brown_scLLC_2.5w <- Brown_scLLC_2.5w@meta.data$orig.ident
labels_Brown_scLLC_3.5w <- Brown_scLLC_3.5w@meta.data$seurat_clusters
samples_Brown_scLLC_3.5w <- Brown_scLLC_3.5w@meta.data$orig.ident
labels_Kim_scB16F10_CTL <- Kim_scB16F10_CTL@meta.data$seurat_clusters
samples_Kim_scB16F10_CTL <- Kim_scB16F10_CTL@meta.data$orig.ident
labels_Kim_scB16F10_B16F10 <- Kim_scB16F10_B16F10@meta.data$seurat_clusters
samples_Kim_scB16F10_B16F10 <- Kim_scB16F10_B16F10@meta.data$orig.ident
labels_Pryce_scC26_CTL <- Pryce_scC26_CTL@meta.data$seurat_clusters
samples_Pryce_scC26_CTL <- Pryce_scC26_CTL@meta.data$orig.ident
labels_Pryce_scC26_C26 <- Pryce_scC26_C26@meta.data$seurat_clusters
samples_Pryce_scC26_C26 <- Pryce_scC26_C26@meta.data$orig.ident
labels_Pryce_scKPP_CTL <- Pryce_scKPP_CTL@meta.data$seurat_clusters
samples_Pryce_scKPP_CTL <- Pryce_scKPP_CTL@meta.data$orig.ident
labels_Pryce_scKPP_KPP <- Pryce_scKPP_KPP@meta.data$seurat_clusters
samples_Pryce_scKPP_KPP <- Pryce_scKPP_KPP@meta.data$orig.ident
labels_Zhang_snKIC_CTL <- Zhang_snKIC_CTL@meta.data$seurat_clusters
samples_Zhang_snKIC_CTL <- Zhang_snKIC_CTL@meta.data$orig.ident
labels_Zhang_snKIC_KIC <- Zhang_snKIC_KIC@meta.data$seurat_clusters
samples_Zhang_snKIC_KIC <- Zhang_snKIC_KIC@meta.data$orig.ident

# === CellChat metadata frames ===
cellchat_Agca_snLLC_CTL_meta <- data.frame(group = labels_Agca_snLLC_CTL, row.names = names(labels_Agca_snLLC_CTL), samples = samples_Agca_snLLC_CTL)
cellchat_Agca_snLLC_LLC_meta <- data.frame(group = labels_Agca_snLLC_LLC, row.names = names(labels_Agca_snLLC_LLC), samples = samples_Agca_snLLC_LLC)
cellchat_Brown_scLLC_CTL_meta <- data.frame(group = labels_Brown_scLLC_CTL, row.names = names(labels_Brown_scLLC_CTL), samples = samples_Brown_scLLC_CTL)
cellchat_Brown_scLLC_2w_meta <- data.frame(group = labels_Brown_scLLC_2w, row.names = names(labels_Brown_scLLC_2w), samples = samples_Brown_scLLC_2w)
cellchat_Brown_scLLC_2.5w_meta <- data.frame(group = labels_Brown_scLLC_2.5w, row.names = names(labels_Brown_scLLC_2.5w), samples = samples_Brown_scLLC_2.5w)
cellchat_Brown_scLLC_3.5w_meta <- data.frame(group = labels_Brown_scLLC_3.5w, row.names = names(labels_Brown_scLLC_3.5w), samples = samples_Brown_scLLC_3.5w)
cellchat_Kim_scB16F10_CTL_meta <- data.frame(group = labels_Kim_scB16F10_CTL, row.names = names(labels_Kim_scB16F10_CTL), samples = samples_Kim_scB16F10_CTL)
cellchat_Kim_scB16F10_B16F10_meta <- data.frame(group = labels_Kim_scB16F10_B16F10, row.names = names(labels_Kim_scB16F10_B16F10), samples = samples_Kim_scB16F10_B16F10)
cellchat_Pryce_scC26_CTL_meta <- data.frame(group = labels_Pryce_scC26_CTL, row.names = names(labels_Pryce_scC26_CTL), samples = samples_Pryce_scC26_CTL)
cellchat_Pryce_scC26_C26_meta <- data.frame(group = labels_Pryce_scC26_C26, row.names = names(labels_Pryce_scC26_C26), samples = samples_Pryce_scC26_C26)
cellchat_Pryce_scKPP_CTL_meta <- data.frame(group = labels_Pryce_scKPP_CTL, row.names = names(labels_Pryce_scKPP_CTL), samples = samples_Pryce_scKPP_CTL)
cellchat_Pryce_scKPP_KPP_meta <- data.frame(group = labels_Pryce_scKPP_KPP, row.names = names(labels_Pryce_scKPP_KPP), samples = samples_Pryce_scKPP_KPP)
cellchat_Zhang_snKIC_CTL_meta <- data.frame(group = labels_Zhang_snKIC_CTL, row.names = names(labels_Zhang_snKIC_CTL), samples = samples_Zhang_snKIC_CTL)
cellchat_Zhang_snKIC_KIC_meta <- data.frame(group = labels_Zhang_snKIC_KIC, row.names = names(labels_Zhang_snKIC_KIC), samples = samples_Zhang_snKIC_KIC)

# === Create CellChat objects ===
cellchat_Agca_snLLC_CTL_all <- createCellChat(object = data_input_Agca_snLLC_CTL, meta = cellchat_Agca_snLLC_CTL_meta, group.by = "group")
cellchat_Agca_snLLC_CTL_secreted <- createCellChat(object = data_input_Agca_snLLC_CTL, meta = cellchat_Agca_snLLC_CTL_meta, group.by = "group")
cellchat_Agca_snLLC_CTL_ECM <- createCellChat(object = data_input_Agca_snLLC_CTL, meta = cellchat_Agca_snLLC_CTL_meta, group.by = "group")
cellchat_Agca_snLLC_CTL_nps <- createCellChat(object = data_input_Agca_snLLC_CTL, meta = cellchat_Agca_snLLC_CTL_meta, group.by = "group")
cellchat_Agca_snLLC_CTL_ccc <- createCellChat(object = data_input_Agca_snLLC_CTL, meta = cellchat_Agca_snLLC_CTL_meta, group.by = "group")

cellchat_Agca_snLLC_LLC_all <- createCellChat(object = data_input_Agca_snLLC_LLC, meta = cellchat_Agca_snLLC_LLC_meta, group.by = "group")
cellchat_Agca_snLLC_LLC_secreted <- createCellChat(object = data_input_Agca_snLLC_LLC, meta = cellchat_Agca_snLLC_LLC_meta, group.by = "group")
cellchat_Agca_snLLC_LLC_ECM <- createCellChat(object = data_input_Agca_snLLC_LLC, meta = cellchat_Agca_snLLC_LLC_meta, group.by = "group")
cellchat_Agca_snLLC_LLC_nps <- createCellChat(object = data_input_Agca_snLLC_LLC, meta = cellchat_Agca_snLLC_LLC_meta, group.by = "group")
cellchat_Agca_snLLC_LLC_ccc <- createCellChat(object = data_input_Agca_snLLC_LLC, meta = cellchat_Agca_snLLC_LLC_meta, group.by = "group")

cellchat_Brown_scLLC_CTL_all <- createCellChat(object = data_input_Brown_scLLC_CTL, meta = cellchat_Brown_scLLC_CTL_meta, group.by = "group")
cellchat_Brown_scLLC_CTL_secreted <- createCellChat(object = data_input_Brown_scLLC_CTL, meta = cellchat_Brown_scLLC_CTL_meta, group.by = "group")
cellchat_Brown_scLLC_CTL_ECM <- createCellChat(object = data_input_Brown_scLLC_CTL, meta = cellchat_Brown_scLLC_CTL_meta, group.by = "group")
cellchat_Brown_scLLC_CTL_nps <- createCellChat(object = data_input_Brown_scLLC_CTL, meta = cellchat_Brown_scLLC_CTL_meta, group.by = "group")
cellchat_Brown_scLLC_CTL_ccc <- createCellChat(object = data_input_Brown_scLLC_CTL, meta = cellchat_Brown_scLLC_CTL_meta, group.by = "group")

cellchat_Brown_scLLC_2w_all <- createCellChat(object = data_input_Brown_scLLC_2w, meta = cellchat_Brown_scLLC_2w_meta, group.by = "group")
cellchat_Brown_scLLC_2w_secreted <- createCellChat(object = data_input_Brown_scLLC_2w, meta = cellchat_Brown_scLLC_2w_meta, group.by = "group")
cellchat_Brown_scLLC_2w_ECM <- createCellChat(object = data_input_Brown_scLLC_2w, meta = cellchat_Brown_scLLC_2w_meta, group.by = "group")
cellchat_Brown_scLLC_2w_nps <- createCellChat(object = data_input_Brown_scLLC_2w, meta = cellchat_Brown_scLLC_2w_meta, group.by = "group")
cellchat_Brown_scLLC_2w_ccc <- createCellChat(object = data_input_Brown_scLLC_2w, meta = cellchat_Brown_scLLC_2w_meta, group.by = "group")

cellchat_Brown_scLLC_2.5w_all <- createCellChat(object = data_input_Brown_scLLC_2.5w, meta = cellchat_Brown_scLLC_2.5w_meta, group.by = "group")
cellchat_Brown_scLLC_2.5w_secreted <- createCellChat(object = data_input_Brown_scLLC_2.5w, meta = cellchat_Brown_scLLC_2.5w_meta, group.by = "group")
cellchat_Brown_scLLC_2.5w_ECM <- createCellChat(object = data_input_Brown_scLLC_2.5w, meta = cellchat_Brown_scLLC_2.5w_meta, group.by = "group")
cellchat_Brown_scLLC_2.5w_nps <- createCellChat(object = data_input_Brown_scLLC_2.5w, meta = cellchat_Brown_scLLC_2.5w_meta, group.by = "group")
cellchat_Brown_scLLC_2.5w_ccc <- createCellChat(object = data_input_Brown_scLLC_2.5w, meta = cellchat_Brown_scLLC_2.5w_meta, group.by = "group")

cellchat_Brown_scLLC_3.5w_all <- createCellChat(object = data_input_Brown_scLLC_3.5w, meta = cellchat_Brown_scLLC_3.5w_meta, group.by = "group")
cellchat_Brown_scLLC_3.5w_secreted <- createCellChat(object = data_input_Brown_scLLC_3.5w, meta = cellchat_Brown_scLLC_3.5w_meta, group.by = "group")
cellchat_Brown_scLLC_3.5w_ECM <- createCellChat(object = data_input_Brown_scLLC_3.5w, meta = cellchat_Brown_scLLC_3.5w_meta, group.by = "group")
cellchat_Brown_scLLC_3.5w_nps <- createCellChat(object = data_input_Brown_scLLC_3.5w, meta = cellchat_Brown_scLLC_3.5w_meta, group.by = "group")
cellchat_Brown_scLLC_3.5w_ccc <- createCellChat(object = data_input_Brown_scLLC_3.5w, meta = cellchat_Brown_scLLC_3.5w_meta, group.by = "group")

cellchat_Kim_scB16F10_CTL_all <- createCellChat(object = data_input_Kim_scB16F10_CTL, meta = cellchat_Kim_scB16F10_CTL_meta, group.by = "group")
cellchat_Kim_scB16F10_CTL_secreted <- createCellChat(object = data_input_Kim_scB16F10_CTL, meta = cellchat_Kim_scB16F10_CTL_meta, group.by = "group")
cellchat_Kim_scB16F10_CTL_ECM <- createCellChat(object = data_input_Kim_scB16F10_CTL, meta = cellchat_Kim_scB16F10_CTL_meta, group.by = "group")
cellchat_Kim_scB16F10_CTL_nps <- createCellChat(object = data_input_Kim_scB16F10_CTL, meta = cellchat_Kim_scB16F10_CTL_meta, group.by = "group")
cellchat_Kim_scB16F10_CTL_ccc <- createCellChat(object = data_input_Kim_scB16F10_CTL, meta = cellchat_Kim_scB16F10_CTL_meta, group.by = "group")

cellchat_Kim_scB16F10_B16F10_all <- createCellChat(object = data_input_Kim_scB16F10_B16F10, meta = cellchat_Kim_scB16F10_B16F10_meta, group.by = "group")
cellchat_Kim_scB16F10_B16F10_secreted <- createCellChat(object = data_input_Kim_scB16F10_B16F10, meta = cellchat_Kim_scB16F10_B16F10_meta, group.by = "group")
cellchat_Kim_scB16F10_B16F10_ECM <- createCellChat(object = data_input_Kim_scB16F10_B16F10, meta = cellchat_Kim_scB16F10_B16F10_meta, group.by = "group")
cellchat_Kim_scB16F10_B16F10_nps <- createCellChat(object = data_input_Kim_scB16F10_B16F10, meta = cellchat_Kim_scB16F10_B16F10_meta, group.by = "group")
cellchat_Kim_scB16F10_B16F10_ccc <- createCellChat(object = data_input_Kim_scB16F10_B16F10, meta = cellchat_Kim_scB16F10_B16F10_meta, group.by = "group")


cellchat_Pryce_scC26_CTL_all <- createCellChat(object = data_input_Pryce_scC26_CTL, meta = cellchat_Pryce_scC26_CTL_meta, group.by = "group")
cellchat_Pryce_scC26_CTL_secreted <- createCellChat(object = data_input_Pryce_scC26_CTL, meta = cellchat_Pryce_scC26_CTL_meta, group.by = "group")
cellchat_Pryce_scC26_CTL_ECM <- createCellChat(object = data_input_Pryce_scC26_CTL, meta = cellchat_Pryce_scC26_CTL_meta, group.by = "group")
cellchat_Pryce_scC26_CTL_nps <- createCellChat(object = data_input_Pryce_scC26_CTL, meta = cellchat_Pryce_scC26_CTL_meta, group.by = "group")
cellchat_Pryce_scC26_CTL_ccc <- createCellChat(object = data_input_Pryce_scC26_CTL, meta = cellchat_Pryce_scC26_CTL_meta, group.by = "group")

cellchat_Pryce_scC26_C26_all <- createCellChat(object = data_input_Pryce_scC26_C26, meta = cellchat_Pryce_scC26_C26_meta, group.by = "group")
cellchat_Pryce_scC26_C26_secreted <- createCellChat(object = data_input_Pryce_scC26_C26, meta = cellchat_Pryce_scC26_C26_meta, group.by = "group")
cellchat_Pryce_scC26_C26_ECM <- createCellChat(object = data_input_Pryce_scC26_C26, meta = cellchat_Pryce_scC26_C26_meta, group.by = "group")
cellchat_Pryce_scC26_C26_nps <- createCellChat(object = data_input_Pryce_scC26_C26, meta = cellchat_Pryce_scC26_C26_meta, group.by = "group")
cellchat_Pryce_scC26_C26_ccc <- createCellChat(object = data_input_Pryce_scC26_C26, meta = cellchat_Pryce_scC26_C26_meta, group.by = "group")

cellchat_Pryce_scKPP_CTL_all <- createCellChat(object = data_input_Pryce_scKPP_CTL, meta = cellchat_Pryce_scKPP_CTL_meta, group.by = "group")
cellchat_Pryce_scKPP_CTL_secreted <- createCellChat(object = data_input_Pryce_scKPP_CTL, meta = cellchat_Pryce_scKPP_CTL_meta, group.by = "group")
cellchat_Pryce_scKPP_CTL_ECM <- createCellChat(object = data_input_Pryce_scKPP_CTL, meta = cellchat_Pryce_scKPP_CTL_meta, group.by = "group")
cellchat_Pryce_scKPP_CTL_nps <- createCellChat(object = data_input_Pryce_scKPP_CTL, meta = cellchat_Pryce_scKPP_CTL_meta, group.by = "group")
cellchat_Pryce_scKPP_CTL_ccc <- createCellChat(object = data_input_Pryce_scKPP_CTL, meta = cellchat_Pryce_scKPP_CTL_meta, group.by = "group")

cellchat_Pryce_scKPP_KPP_all <- createCellChat(object = data_input_Pryce_scKPP_KPP, meta = cellchat_Pryce_scKPP_KPP_meta, group.by = "group")
cellchat_Pryce_scKPP_KPP_secreted <- createCellChat(object = data_input_Pryce_scKPP_KPP, meta = cellchat_Pryce_scKPP_KPP_meta, group.by = "group")
cellchat_Pryce_scKPP_KPP_ECM <- createCellChat(object = data_input_Pryce_scKPP_KPP, meta = cellchat_Pryce_scKPP_KPP_meta, group.by = "group")
cellchat_Pryce_scKPP_KPP_nps <- createCellChat(object = data_input_Pryce_scKPP_KPP, meta = cellchat_Pryce_scKPP_KPP_meta, group.by = "group")
cellchat_Pryce_scKPP_KPP_ccc <- createCellChat(object = data_input_Pryce_scKPP_KPP, meta = cellchat_Pryce_scKPP_KPP_meta, group.by = "group")

cellchat_Zhang_snKIC_CTL_all <- createCellChat(object = data_input_Zhang_snKIC_CTL, meta = cellchat_Zhang_snKIC_CTL_meta, group.by = "group")
cellchat_Zhang_snKIC_CTL_secreted <- createCellChat(object = data_input_Zhang_snKIC_CTL, meta = cellchat_Zhang_snKIC_CTL_meta, group.by = "group")
cellchat_Zhang_snKIC_CTL_ECM <- createCellChat(object = data_input_Zhang_snKIC_CTL, meta = cellchat_Zhang_snKIC_CTL_meta, group.by = "group")
cellchat_Zhang_snKIC_CTL_nps <- createCellChat(object = data_input_Zhang_snKIC_CTL, meta = cellchat_Zhang_snKIC_CTL_meta, group.by = "group")
cellchat_Zhang_snKIC_CTL_ccc <- createCellChat(object = data_input_Zhang_snKIC_CTL, meta = cellchat_Zhang_snKIC_CTL_meta, group.by = "group")

cellchat_Zhang_snKIC_KIC_all <- createCellChat(object = data_input_Zhang_snKIC_KIC, meta = cellchat_Zhang_snKIC_KIC_meta, group.by = "group")
cellchat_Zhang_snKIC_KIC_secreted <- createCellChat(object = data_input_Zhang_snKIC_KIC, meta = cellchat_Zhang_snKIC_KIC_meta, group.by = "group")
cellchat_Zhang_snKIC_KIC_ECM <- createCellChat(object = data_input_Zhang_snKIC_KIC, meta = cellchat_Zhang_snKIC_KIC_meta, group.by = "group")
cellchat_Zhang_snKIC_KIC_nps <- createCellChat(object = data_input_Zhang_snKIC_KIC, meta = cellchat_Zhang_snKIC_KIC_meta, group.by = "group")
cellchat_Zhang_snKIC_KIC_ccc <- createCellChat(object = data_input_Zhang_snKIC_KIC, meta = cellchat_Zhang_snKIC_KIC_meta, group.by = "group")
```



# Set which CellChat database to use

```{r, include = FALSE}
cellchat_Agca_snLLC_CTL_all@DB <- CellChatDB.mouse
cellchat_Agca_snLLC_CTL_secreted@DB <- CellChatDB.mouse
cellchat_Agca_snLLC_CTL_ECM@DB <- CellChatDB.mouse
cellchat_Agca_snLLC_CTL_nps@DB <- CellChatDB.mouse
cellchat_Agca_snLLC_CTL_ccc@DB <- CellChatDB.mouse

cellchat_Agca_snLLC_LLC_all@DB <- CellChatDB.mouse
cellchat_Agca_snLLC_LLC_secreted@DB <- CellChatDB.mouse
cellchat_Agca_snLLC_LLC_ECM@DB <- CellChatDB.mouse
cellchat_Agca_snLLC_LLC_nps@DB <- CellChatDB.mouse
cellchat_Agca_snLLC_LLC_ccc@DB <- CellChatDB.mouse

cellchat_Brown_scLLC_CTL_all@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_CTL_secreted@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_CTL_ECM@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_CTL_nps@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_CTL_ccc@DB <- CellChatDB.mouse

cellchat_Brown_scLLC_2w_all@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_2w_secreted@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_2w_ECM@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_2w_nps@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_2w_ccc@DB <- CellChatDB.mouse

cellchat_Brown_scLLC_2.5w_all@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_2.5w_secreted@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_2.5w_ECM@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_2.5w_nps@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_2.5w_ccc@DB <- CellChatDB.mouse

cellchat_Brown_scLLC_3.5w_all@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_3.5w_secreted@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_3.5w_ECM@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_3.5w_nps@DB <- CellChatDB.mouse
cellchat_Brown_scLLC_3.5w_ccc@DB <- CellChatDB.mouse

cellchat_Kim_scB16F10_CTL_all@DB <- CellChatDB.mouse
cellchat_Kim_scB16F10_CTL_secreted@DB <- CellChatDB.mouse
cellchat_Kim_scB16F10_CTL_ECM@DB <- CellChatDB.mouse
cellchat_Kim_scB16F10_CTL_nps@DB <- CellChatDB.mouse
cellchat_Kim_scB16F10_CTL_ccc@DB <- CellChatDB.mouse

cellchat_Kim_scB16F10_B16F10_all@DB <- CellChatDB.mouse
cellchat_Kim_scB16F10_B16F10_secreted@DB <- CellChatDB.mouse
cellchat_Kim_scB16F10_B16F10_ECM@DB <- CellChatDB.mouse
cellchat_Kim_scB16F10_B16F10_nps@DB <- CellChatDB.mouse
cellchat_Kim_scB16F10_B16F10_ccc@DB <- CellChatDB.mouse


cellchat_Pryce_scC26_CTL_all@DB <- CellChatDB.mouse
cellchat_Pryce_scC26_CTL_secreted@DB <- CellChatDB.mouse
cellchat_Pryce_scC26_CTL_ECM@DB <- CellChatDB.mouse
cellchat_Pryce_scC26_CTL_nps@DB <- CellChatDB.mouse
cellchat_Pryce_scC26_CTL_ccc@DB <- CellChatDB.mouse

cellchat_Pryce_scC26_C26_all@DB <- CellChatDB.mouse
cellchat_Pryce_scC26_C26_secreted@DB <- CellChatDB.mouse
cellchat_Pryce_scC26_C26_ECM@DB <- CellChatDB.mouse
cellchat_Pryce_scC26_C26_nps@DB <- CellChatDB.mouse
cellchat_Pryce_scC26_C26_ccc@DB <- CellChatDB.mouse

cellchat_Pryce_scKPP_CTL_all@DB <- CellChatDB.mouse
cellchat_Pryce_scKPP_CTL_secreted@DB <- CellChatDB.mouse
cellchat_Pryce_scKPP_CTL_ECM@DB <- CellChatDB.mouse
cellchat_Pryce_scKPP_CTL_nps@DB <- CellChatDB.mouse
cellchat_Pryce_scKPP_CTL_ccc@DB <- CellChatDB.mouse

cellchat_Pryce_scKPP_KPP_all@DB <- CellChatDB.mouse
cellchat_Pryce_scKPP_KPP_secreted@DB <- CellChatDB.mouse
cellchat_Pryce_scKPP_KPP_ECM@DB <- CellChatDB.mouse
cellchat_Pryce_scKPP_KPP_nps@DB <- CellChatDB.mouse
cellchat_Pryce_scKPP_KPP_ccc@DB <- CellChatDB.mouse

cellchat_Zhang_snKIC_CTL_all@DB <- CellChatDB.mouse
cellchat_Zhang_snKIC_CTL_secreted@DB <- CellChatDB.mouse
cellchat_Zhang_snKIC_CTL_ECM@DB <- CellChatDB.mouse
cellchat_Zhang_snKIC_CTL_nps@DB <- CellChatDB.mouse
cellchat_Zhang_snKIC_CTL_ccc@DB <- CellChatDB.mouse

cellchat_Zhang_snKIC_KIC_all@DB <- CellChatDB.mouse
cellchat_Zhang_snKIC_KIC_secreted@DB <- CellChatDB.mouse
cellchat_Zhang_snKIC_KIC_ECM@DB <- CellChatDB.mouse
cellchat_Zhang_snKIC_KIC_nps@DB <- CellChatDB.mouse
cellchat_Zhang_snKIC_KIC_ccc@DB <- CellChatDB.mouse
```



# Subset for each interaction type

```{r, include=FALSE}
# === Define database subsets ===
CellChatDB_secreted <- subsetDB(CellChatDB.mouse, search = "Secreted Signaling")
CellChatDB_ECM <- subsetDB(CellChatDB.mouse, search = "ECM-Receptor")
CellChatDB_nps <- subsetDB(CellChatDB.mouse, search = "Non-protein Signaling")
CellChatDB_ccc <- subsetDB(CellChatDB.mouse, search = "Cell-Cell Contact")

# === Assign subset DBs to each CellChat object ===
cellchat_Agca_snLLC_CTL_secreted@DB <- CellChatDB_secreted
cellchat_Agca_snLLC_CTL_ECM@DB <- CellChatDB_ECM
cellchat_Agca_snLLC_CTL_nps@DB <- CellChatDB_nps
cellchat_Agca_snLLC_CTL_ccc@DB <- CellChatDB_ccc

cellchat_Agca_snLLC_LLC_secreted@DB <- CellChatDB_secreted
cellchat_Agca_snLLC_LLC_ECM@DB <- CellChatDB_ECM
cellchat_Agca_snLLC_LLC_nps@DB <- CellChatDB_nps
cellchat_Agca_snLLC_LLC_ccc@DB <- CellChatDB_ccc

cellchat_Brown_scLLC_CTL_secreted@DB <- CellChatDB_secreted
cellchat_Brown_scLLC_CTL_ECM@DB <- CellChatDB_ECM
cellchat_Brown_scLLC_CTL_nps@DB <- CellChatDB_nps
cellchat_Brown_scLLC_CTL_ccc@DB <- CellChatDB_ccc

cellchat_Brown_scLLC_2w_secreted@DB <- CellChatDB_secreted
cellchat_Brown_scLLC_2w_ECM@DB <- CellChatDB_ECM
cellchat_Brown_scLLC_2w_nps@DB <- CellChatDB_nps
cellchat_Brown_scLLC_2w_ccc@DB <- CellChatDB_ccc

cellchat_Brown_scLLC_2.5w_secreted@DB <- CellChatDB_secreted
cellchat_Brown_scLLC_2.5w_ECM@DB <- CellChatDB_ECM
cellchat_Brown_scLLC_2.5w_nps@DB <- CellChatDB_nps
cellchat_Brown_scLLC_2.5w_ccc@DB <- CellChatDB_ccc

cellchat_Brown_scLLC_3.5w_secreted@DB <- CellChatDB_secreted
cellchat_Brown_scLLC_3.5w_ECM@DB <- CellChatDB_ECM
cellchat_Brown_scLLC_3.5w_nps@DB <- CellChatDB_nps
cellchat_Brown_scLLC_3.5w_ccc@DB <- CellChatDB_ccc

cellchat_Kim_scB16F10_CTL_secreted@DB <- CellChatDB_secreted
cellchat_Kim_scB16F10_CTL_ECM@DB <- CellChatDB_ECM
cellchat_Kim_scB16F10_CTL_nps@DB <- CellChatDB_nps
cellchat_Kim_scB16F10_CTL_ccc@DB <- CellChatDB_ccc

cellchat_Kim_scB16F10_B16F10_secreted@DB <- CellChatDB_secreted
cellchat_Kim_scB16F10_B16F10_ECM@DB <- CellChatDB_ECM
cellchat_Kim_scB16F10_B16F10_nps@DB <- CellChatDB_nps
cellchat_Kim_scB16F10_B16F10_ccc@DB <- CellChatDB_ccc

cellchat_Pryce_scC26_CTL_secreted@DB <- CellChatDB_secreted
cellchat_Pryce_scC26_CTL_ECM@DB <- CellChatDB_ECM
cellchat_Pryce_scC26_CTL_nps@DB <- CellChatDB_nps
cellchat_Pryce_scC26_CTL_ccc@DB <- CellChatDB_ccc

cellchat_Pryce_scC26_C26_secreted@DB <- CellChatDB_secreted
cellchat_Pryce_scC26_C26_ECM@DB <- CellChatDB_ECM
cellchat_Pryce_scC26_C26_nps@DB <- CellChatDB_nps
cellchat_Pryce_scC26_C26_ccc@DB <- CellChatDB_ccc

cellchat_Pryce_scKPP_CTL_secreted@DB <- CellChatDB_secreted
cellchat_Pryce_scKPP_CTL_ECM@DB <- CellChatDB_ECM
cellchat_Pryce_scKPP_CTL_nps@DB <- CellChatDB_nps
cellchat_Pryce_scKPP_CTL_ccc@DB <- CellChatDB_ccc

cellchat_Pryce_scKPP_KPP_secreted@DB <- CellChatDB_secreted
cellchat_Pryce_scKPP_KPP_ECM@DB <- CellChatDB_ECM
cellchat_Pryce_scKPP_KPP_nps@DB <- CellChatDB_nps
cellchat_Pryce_scKPP_KPP_ccc@DB <- CellChatDB_ccc

cellchat_Zhang_snKIC_CTL_secreted@DB <- CellChatDB_secreted
cellchat_Zhang_snKIC_CTL_ECM@DB <- CellChatDB_ECM
cellchat_Zhang_snKIC_CTL_nps@DB <- CellChatDB_nps
cellchat_Zhang_snKIC_CTL_ccc@DB <- CellChatDB_ccc

cellchat_Zhang_snKIC_KIC_secreted@DB <- CellChatDB_secreted
cellchat_Zhang_snKIC_KIC_ECM@DB <- CellChatDB_ECM
cellchat_Zhang_snKIC_KIC_nps@DB <- CellChatDB_nps
cellchat_Zhang_snKIC_KIC_ccc@DB <- CellChatDB_ccc
```



# Subset expression data of signaling genes

```{r, include=FALSE}
# --- Agca_snLLC_CTL ---
cellchat_Agca_snLLC_CTL_all <- subsetData(cellchat_Agca_snLLC_CTL_all)
cellchat_Agca_snLLC_CTL_secreted <- subsetData(cellchat_Agca_snLLC_CTL_secreted)
cellchat_Agca_snLLC_CTL_ECM <- subsetData(cellchat_Agca_snLLC_CTL_ECM)
cellchat_Agca_snLLC_CTL_nps <- subsetData(cellchat_Agca_snLLC_CTL_nps)
cellchat_Agca_snLLC_CTL_ccc <- subsetData(cellchat_Agca_snLLC_CTL_ccc)

# --- Agca_snLLC_LLC ---
cellchat_Agca_snLLC_LLC_all <- subsetData(cellchat_Agca_snLLC_LLC_all)
cellchat_Agca_snLLC_LLC_secreted <- subsetData(cellchat_Agca_snLLC_LLC_secreted)
cellchat_Agca_snLLC_LLC_ECM <- subsetData(cellchat_Agca_snLLC_LLC_ECM)
cellchat_Agca_snLLC_LLC_nps <- subsetData(cellchat_Agca_snLLC_LLC_nps)
cellchat_Agca_snLLC_LLC_ccc <- subsetData(cellchat_Agca_snLLC_LLC_ccc)

# --- Brown_scLLC_CTL ---
cellchat_Brown_scLLC_CTL_all <- subsetData(cellchat_Brown_scLLC_CTL_all)
cellchat_Brown_scLLC_CTL_secreted <- subsetData(cellchat_Brown_scLLC_CTL_secreted)
cellchat_Brown_scLLC_CTL_ECM <- subsetData(cellchat_Brown_scLLC_CTL_ECM)
cellchat_Brown_scLLC_CTL_nps <- subsetData(cellchat_Brown_scLLC_CTL_nps)
cellchat_Brown_scLLC_CTL_ccc <- subsetData(cellchat_Brown_scLLC_CTL_ccc)

# --- Brown_scLLC_2w ---
cellchat_Brown_scLLC_2w_all <- subsetData(cellchat_Brown_scLLC_2w_all)
cellchat_Brown_scLLC_2w_secreted <- subsetData(cellchat_Brown_scLLC_2w_secreted)
cellchat_Brown_scLLC_2w_ECM <- subsetData(cellchat_Brown_scLLC_2w_ECM)
cellchat_Brown_scLLC_2w_nps <- subsetData(cellchat_Brown_scLLC_2w_nps)
cellchat_Brown_scLLC_2w_ccc <- subsetData(cellchat_Brown_scLLC_2w_ccc)

# --- Brown_scLLC_2.5w ---
cellchat_Brown_scLLC_2.5w_all <- subsetData(cellchat_Brown_scLLC_2.5w_all)
cellchat_Brown_scLLC_2.5w_secreted <- subsetData(cellchat_Brown_scLLC_2.5w_secreted)
cellchat_Brown_scLLC_2.5w_ECM <- subsetData(cellchat_Brown_scLLC_2.5w_ECM)
cellchat_Brown_scLLC_2.5w_nps <- subsetData(cellchat_Brown_scLLC_2.5w_nps)
cellchat_Brown_scLLC_2.5w_ccc <- subsetData(cellchat_Brown_scLLC_2.5w_ccc)

# --- Brown_scLLC_3.5w ---
cellchat_Brown_scLLC_3.5w_all <- subsetData(cellchat_Brown_scLLC_3.5w_all)
cellchat_Brown_scLLC_3.5w_secreted <- subsetData(cellchat_Brown_scLLC_3.5w_secreted)
cellchat_Brown_scLLC_3.5w_ECM <- subsetData(cellchat_Brown_scLLC_3.5w_ECM)
cellchat_Brown_scLLC_3.5w_nps <- subsetData(cellchat_Brown_scLLC_3.5w_nps)
cellchat_Brown_scLLC_3.5w_ccc <- subsetData(cellchat_Brown_scLLC_3.5w_ccc)

# --- Kim_scB16F10_CTL ---
cellchat_Kim_scB16F10_CTL_all <- subsetData(cellchat_Kim_scB16F10_CTL_all)
cellchat_Kim_scB16F10_CTL_secreted <- subsetData(cellchat_Kim_scB16F10_CTL_secreted)
cellchat_Kim_scB16F10_CTL_ECM <- subsetData(cellchat_Kim_scB16F10_CTL_ECM)
cellchat_Kim_scB16F10_CTL_nps <- subsetData(cellchat_Kim_scB16F10_CTL_nps)
cellchat_Kim_scB16F10_CTL_ccc <- subsetData(cellchat_Kim_scB16F10_CTL_ccc)

# --- Kim_scB16F10_B16F10 ---
cellchat_Kim_scB16F10_B16F10_all <- subsetData(cellchat_Kim_scB16F10_B16F10_all)
cellchat_Kim_scB16F10_B16F10_secreted <- subsetData(cellchat_Kim_scB16F10_B16F10_secreted)
cellchat_Kim_scB16F10_B16F10_ECM <- subsetData(cellchat_Kim_scB16F10_B16F10_ECM)
cellchat_Kim_scB16F10_B16F10_nps <- subsetData(cellchat_Kim_scB16F10_B16F10_nps)
cellchat_Kim_scB16F10_B16F10_ccc <- subsetData(cellchat_Kim_scB16F10_B16F10_ccc)

# --- Pryce_scC26_CTL ---
cellchat_Pryce_scC26_CTL_all <- subsetData(cellchat_Pryce_scC26_CTL_all)
cellchat_Pryce_scC26_CTL_secreted <- subsetData(cellchat_Pryce_scC26_CTL_secreted)
cellchat_Pryce_scC26_CTL_ECM <- subsetData(cellchat_Pryce_scC26_CTL_ECM)
cellchat_Pryce_scC26_CTL_nps <- subsetData(cellchat_Pryce_scC26_CTL_nps)
cellchat_Pryce_scC26_CTL_ccc <- subsetData(cellchat_Pryce_scC26_CTL_ccc)

# --- Pryce_scC26_C26 ---
cellchat_Pryce_scC26_C26_all <- subsetData(cellchat_Pryce_scC26_C26_all)
cellchat_Pryce_scC26_C26_secreted <- subsetData(cellchat_Pryce_scC26_C26_secreted)
cellchat_Pryce_scC26_C26_ECM <- subsetData(cellchat_Pryce_scC26_C26_ECM)
cellchat_Pryce_scC26_C26_nps <- subsetData(cellchat_Pryce_scC26_C26_nps)
cellchat_Pryce_scC26_C26_ccc <- subsetData(cellchat_Pryce_scC26_C26_ccc)

# --- Pryce_scKPP_CTL ---
cellchat_Pryce_scKPP_CTL_all <- subsetData(cellchat_Pryce_scKPP_CTL_all)
cellchat_Pryce_scKPP_CTL_secreted <- subsetData(cellchat_Pryce_scKPP_CTL_secreted)
cellchat_Pryce_scKPP_CTL_ECM <- subsetData(cellchat_Pryce_scKPP_CTL_ECM)
cellchat_Pryce_scKPP_CTL_nps <- subsetData(cellchat_Pryce_scKPP_CTL_nps)
cellchat_Pryce_scKPP_CTL_ccc <- subsetData(cellchat_Pryce_scKPP_CTL_ccc)

# --- Pryce_scKPP_KPP ---
cellchat_Pryce_scKPP_KPP_all <- subsetData(cellchat_Pryce_scKPP_KPP_all)
cellchat_Pryce_scKPP_KPP_secreted <- subsetData(cellchat_Pryce_scKPP_KPP_secreted)
cellchat_Pryce_scKPP_KPP_ECM <- subsetData(cellchat_Pryce_scKPP_KPP_ECM)
cellchat_Pryce_scKPP_KPP_nps <- subsetData(cellchat_Pryce_scKPP_KPP_nps)
cellchat_Pryce_scKPP_KPP_ccc <- subsetData(cellchat_Pryce_scKPP_KPP_ccc)

# --- Zhang_snKIC_CTL ---
cellchat_Zhang_snKIC_CTL_all <- subsetData(cellchat_Zhang_snKIC_CTL_all)
cellchat_Zhang_snKIC_CTL_secreted <- subsetData(cellchat_Zhang_snKIC_CTL_secreted)
cellchat_Zhang_snKIC_CTL_ECM <- subsetData(cellchat_Zhang_snKIC_CTL_ECM)
cellchat_Zhang_snKIC_CTL_nps <- subsetData(cellchat_Zhang_snKIC_CTL_nps)
cellchat_Zhang_snKIC_CTL_ccc <- subsetData(cellchat_Zhang_snKIC_CTL_ccc)

# --- Zhang_snKIC_KIC ---
cellchat_Zhang_snKIC_KIC_all <- subsetData(cellchat_Zhang_snKIC_KIC_all)
cellchat_Zhang_snKIC_KIC_secreted <- subsetData(cellchat_Zhang_snKIC_KIC_secreted)
cellchat_Zhang_snKIC_KIC_ECM <- subsetData(cellchat_Zhang_snKIC_KIC_ECM)
cellchat_Zhang_snKIC_KIC_nps <- subsetData(cellchat_Zhang_snKIC_KIC_nps)
cellchat_Zhang_snKIC_KIC_ccc <- subsetData(cellchat_Zhang_snKIC_KIC_ccc)
```



# CellChat processing

```{r, include=FALSE}
# === identifyOverExpressedGenes ===
cellchat_Agca_snLLC_CTL_all <- identifyOverExpressedGenes(cellchat_Agca_snLLC_CTL_all)
cellchat_Agca_snLLC_CTL_secreted <- identifyOverExpressedGenes(cellchat_Agca_snLLC_CTL_secreted)
cellchat_Agca_snLLC_CTL_ECM <- identifyOverExpressedGenes(cellchat_Agca_snLLC_CTL_ECM)
cellchat_Agca_snLLC_CTL_nps <- identifyOverExpressedGenes(cellchat_Agca_snLLC_CTL_nps)
cellchat_Agca_snLLC_CTL_ccc <- identifyOverExpressedGenes(cellchat_Agca_snLLC_CTL_ccc)

cellchat_Agca_snLLC_LLC_all <- identifyOverExpressedGenes(cellchat_Agca_snLLC_LLC_all)
cellchat_Agca_snLLC_LLC_secreted <- identifyOverExpressedGenes(cellchat_Agca_snLLC_LLC_secreted)
cellchat_Agca_snLLC_LLC_ECM <- identifyOverExpressedGenes(cellchat_Agca_snLLC_LLC_ECM)
cellchat_Agca_snLLC_LLC_nps <- identifyOverExpressedGenes(cellchat_Agca_snLLC_LLC_nps)
cellchat_Agca_snLLC_LLC_ccc <- identifyOverExpressedGenes(cellchat_Agca_snLLC_LLC_ccc)

cellchat_Brown_scLLC_CTL_all <- identifyOverExpressedGenes(cellchat_Brown_scLLC_CTL_all)
cellchat_Brown_scLLC_CTL_secreted <- identifyOverExpressedGenes(cellchat_Brown_scLLC_CTL_secreted)
cellchat_Brown_scLLC_CTL_ECM <- identifyOverExpressedGenes(cellchat_Brown_scLLC_CTL_ECM)
cellchat_Brown_scLLC_CTL_nps <- identifyOverExpressedGenes(cellchat_Brown_scLLC_CTL_nps)
cellchat_Brown_scLLC_CTL_ccc <- identifyOverExpressedGenes(cellchat_Brown_scLLC_CTL_ccc)

cellchat_Brown_scLLC_2w_all <- identifyOverExpressedGenes(cellchat_Brown_scLLC_2w_all)
cellchat_Brown_scLLC_2w_secreted <- identifyOverExpressedGenes(cellchat_Brown_scLLC_2w_secreted)
cellchat_Brown_scLLC_2w_ECM <- identifyOverExpressedGenes(cellchat_Brown_scLLC_2w_ECM)
cellchat_Brown_scLLC_2w_nps <- identifyOverExpressedGenes(cellchat_Brown_scLLC_2w_nps)
cellchat_Brown_scLLC_2w_ccc <- identifyOverExpressedGenes(cellchat_Brown_scLLC_2w_ccc)

cellchat_Brown_scLLC_2.5w_all <- identifyOverExpressedGenes(cellchat_Brown_scLLC_2.5w_all)
cellchat_Brown_scLLC_2.5w_secreted <- identifyOverExpressedGenes(cellchat_Brown_scLLC_2.5w_secreted)
cellchat_Brown_scLLC_2.5w_ECM <- identifyOverExpressedGenes(cellchat_Brown_scLLC_2.5w_ECM)
cellchat_Brown_scLLC_2.5w_nps <- identifyOverExpressedGenes(cellchat_Brown_scLLC_2.5w_nps)
cellchat_Brown_scLLC_2.5w_ccc <- identifyOverExpressedGenes(cellchat_Brown_scLLC_2.5w_ccc)

cellchat_Brown_scLLC_3.5w_all <- identifyOverExpressedGenes(cellchat_Brown_scLLC_3.5w_all)
cellchat_Brown_scLLC_3.5w_secreted <- identifyOverExpressedGenes(cellchat_Brown_scLLC_3.5w_secreted)
cellchat_Brown_scLLC_3.5w_ECM <- identifyOverExpressedGenes(cellchat_Brown_scLLC_3.5w_ECM)
cellchat_Brown_scLLC_3.5w_nps <- identifyOverExpressedGenes(cellchat_Brown_scLLC_3.5w_nps)
cellchat_Brown_scLLC_3.5w_ccc <- identifyOverExpressedGenes(cellchat_Brown_scLLC_3.5w_ccc)

cellchat_Kim_scB16F10_CTL_all <- identifyOverExpressedGenes(cellchat_Kim_scB16F10_CTL_all)
cellchat_Kim_scB16F10_CTL_secreted <- identifyOverExpressedGenes(cellchat_Kim_scB16F10_CTL_secreted)
cellchat_Kim_scB16F10_CTL_ECM <- identifyOverExpressedGenes(cellchat_Kim_scB16F10_CTL_ECM)
cellchat_Kim_scB16F10_CTL_nps <- identifyOverExpressedGenes(cellchat_Kim_scB16F10_CTL_nps)
cellchat_Kim_scB16F10_CTL_ccc <- identifyOverExpressedGenes(cellchat_Kim_scB16F10_CTL_ccc)

cellchat_Kim_scB16F10_B16F10_all <- identifyOverExpressedGenes(cellchat_Kim_scB16F10_B16F10_all)
cellchat_Kim_scB16F10_B16F10_secreted <- identifyOverExpressedGenes(cellchat_Kim_scB16F10_B16F10_secreted)
cellchat_Kim_scB16F10_B16F10_ECM <- identifyOverExpressedGenes(cellchat_Kim_scB16F10_B16F10_ECM)
cellchat_Kim_scB16F10_B16F10_nps <- identifyOverExpressedGenes(cellchat_Kim_scB16F10_B16F10_nps)
cellchat_Kim_scB16F10_B16F10_ccc <- identifyOverExpressedGenes(cellchat_Kim_scB16F10_B16F10_ccc)

cellchat_Pryce_scC26_CTL_all <- identifyOverExpressedGenes(cellchat_Pryce_scC26_CTL_all)
cellchat_Pryce_scC26_CTL_secreted <- identifyOverExpressedGenes(cellchat_Pryce_scC26_CTL_secreted)
cellchat_Pryce_scC26_CTL_ECM <- identifyOverExpressedGenes(cellchat_Pryce_scC26_CTL_ECM)
cellchat_Pryce_scC26_CTL_nps <- identifyOverExpressedGenes(cellchat_Pryce_scC26_CTL_nps)
cellchat_Pryce_scC26_CTL_ccc <- identifyOverExpressedGenes(cellchat_Pryce_scC26_CTL_ccc)

cellchat_Pryce_scC26_C26_all <- identifyOverExpressedGenes(cellchat_Pryce_scC26_C26_all)
cellchat_Pryce_scC26_C26_secreted <- identifyOverExpressedGenes(cellchat_Pryce_scC26_C26_secreted)
cellchat_Pryce_scC26_C26_ECM <- identifyOverExpressedGenes(cellchat_Pryce_scC26_C26_ECM)
cellchat_Pryce_scC26_C26_nps <- identifyOverExpressedGenes(cellchat_Pryce_scC26_C26_nps)
cellchat_Pryce_scC26_C26_ccc <- identifyOverExpressedGenes(cellchat_Pryce_scC26_C26_ccc)

cellchat_Pryce_scKPP_CTL_all <- identifyOverExpressedGenes(cellchat_Pryce_scKPP_CTL_all)
cellchat_Pryce_scKPP_CTL_secreted <- identifyOverExpressedGenes(cellchat_Pryce_scKPP_CTL_secreted)
cellchat_Pryce_scKPP_CTL_ECM <- identifyOverExpressedGenes(cellchat_Pryce_scKPP_CTL_ECM)
cellchat_Pryce_scKPP_CTL_nps <- identifyOverExpressedGenes(cellchat_Pryce_scKPP_CTL_nps)
cellchat_Pryce_scKPP_CTL_ccc <- identifyOverExpressedGenes(cellchat_Pryce_scKPP_CTL_ccc)

cellchat_Pryce_scKPP_KPP_all <- identifyOverExpressedGenes(cellchat_Pryce_scKPP_KPP_all)
cellchat_Pryce_scKPP_KPP_secreted <- identifyOverExpressedGenes(cellchat_Pryce_scKPP_KPP_secreted)
cellchat_Pryce_scKPP_KPP_ECM <- identifyOverExpressedGenes(cellchat_Pryce_scKPP_KPP_ECM)
cellchat_Pryce_scKPP_KPP_nps <- identifyOverExpressedGenes(cellchat_Pryce_scKPP_KPP_nps)
cellchat_Pryce_scKPP_KPP_ccc <- identifyOverExpressedGenes(cellchat_Pryce_scKPP_KPP_ccc)

cellchat_Zhang_snKIC_CTL_all <- identifyOverExpressedGenes(cellchat_Zhang_snKIC_CTL_all)
cellchat_Zhang_snKIC_CTL_secreted <- identifyOverExpressedGenes(cellchat_Zhang_snKIC_CTL_secreted)
cellchat_Zhang_snKIC_CTL_ECM <- identifyOverExpressedGenes(cellchat_Zhang_snKIC_CTL_ECM)
cellchat_Zhang_snKIC_CTL_nps <- identifyOverExpressedGenes(cellchat_Zhang_snKIC_CTL_nps)
cellchat_Zhang_snKIC_CTL_ccc <- identifyOverExpressedGenes(cellchat_Zhang_snKIC_CTL_ccc)

cellchat_Zhang_snKIC_KIC_all <- identifyOverExpressedGenes(cellchat_Zhang_snKIC_KIC_all)
cellchat_Zhang_snKIC_KIC_secreted <- identifyOverExpressedGenes(cellchat_Zhang_snKIC_KIC_secreted)
cellchat_Zhang_snKIC_KIC_ECM <- identifyOverExpressedGenes(cellchat_Zhang_snKIC_KIC_ECM)
cellchat_Zhang_snKIC_KIC_nps <- identifyOverExpressedGenes(cellchat_Zhang_snKIC_KIC_nps)
cellchat_Zhang_snKIC_KIC_ccc <- identifyOverExpressedGenes(cellchat_Zhang_snKIC_KIC_ccc)

# === identifyOverExpressedInteractions ===
cellchat_Agca_snLLC_CTL_all <- identifyOverExpressedInteractions(cellchat_Agca_snLLC_CTL_all)
cellchat_Agca_snLLC_CTL_secreted <- identifyOverExpressedInteractions(cellchat_Agca_snLLC_CTL_secreted)
cellchat_Agca_snLLC_CTL_ECM <- identifyOverExpressedInteractions(cellchat_Agca_snLLC_CTL_ECM)
cellchat_Agca_snLLC_CTL_nps <- identifyOverExpressedInteractions(cellchat_Agca_snLLC_CTL_nps)
cellchat_Agca_snLLC_CTL_ccc <- identifyOverExpressedInteractions(cellchat_Agca_snLLC_CTL_ccc)

cellchat_Agca_snLLC_LLC_all <- identifyOverExpressedInteractions(cellchat_Agca_snLLC_LLC_all)
cellchat_Agca_snLLC_LLC_secreted <- identifyOverExpressedInteractions(cellchat_Agca_snLLC_LLC_secreted)
cellchat_Agca_snLLC_LLC_ECM <- identifyOverExpressedInteractions(cellchat_Agca_snLLC_LLC_ECM)
cellchat_Agca_snLLC_LLC_nps <- identifyOverExpressedInteractions(cellchat_Agca_snLLC_LLC_nps)
cellchat_Agca_snLLC_LLC_ccc <- identifyOverExpressedInteractions(cellchat_Agca_snLLC_LLC_ccc)

cellchat_Brown_scLLC_CTL_all <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_CTL_all)
cellchat_Brown_scLLC_CTL_secreted <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_CTL_secreted)
cellchat_Brown_scLLC_CTL_ECM <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_CTL_ECM)
cellchat_Brown_scLLC_CTL_nps <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_CTL_nps)
cellchat_Brown_scLLC_CTL_ccc <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_CTL_ccc)

cellchat_Brown_scLLC_2w_all <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_2w_all)
cellchat_Brown_scLLC_2w_secreted <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_2w_secreted)
cellchat_Brown_scLLC_2w_ECM <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_2w_ECM)
cellchat_Brown_scLLC_2w_nps <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_2w_nps)
cellchat_Brown_scLLC_2w_ccc <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_2w_ccc)

cellchat_Brown_scLLC_2.5w_all <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_2.5w_all)
cellchat_Brown_scLLC_2.5w_secreted <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_2.5w_secreted)
cellchat_Brown_scLLC_2.5w_ECM <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_2.5w_ECM)
cellchat_Brown_scLLC_2.5w_nps <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_2.5w_nps)
cellchat_Brown_scLLC_2.5w_ccc <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_2.5w_ccc)

cellchat_Brown_scLLC_3.5w_all <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_3.5w_all)
cellchat_Brown_scLLC_3.5w_secreted <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_3.5w_secreted)
cellchat_Brown_scLLC_3.5w_ECM <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_3.5w_ECM)
cellchat_Brown_scLLC_3.5w_nps <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_3.5w_nps)
cellchat_Brown_scLLC_3.5w_ccc <- identifyOverExpressedInteractions(cellchat_Brown_scLLC_3.5w_ccc)

cellchat_Kim_scB16F10_CTL_all <- identifyOverExpressedInteractions(cellchat_Kim_scB16F10_CTL_all)
cellchat_Kim_scB16F10_CTL_secreted <- identifyOverExpressedInteractions(cellchat_Kim_scB16F10_CTL_secreted)
cellchat_Kim_scB16F10_CTL_ECM <- identifyOverExpressedInteractions(cellchat_Kim_scB16F10_CTL_ECM)
cellchat_Kim_scB16F10_CTL_nps <- identifyOverExpressedInteractions(cellchat_Kim_scB16F10_CTL_nps)
cellchat_Kim_scB16F10_CTL_ccc <- identifyOverExpressedInteractions(cellchat_Kim_scB16F10_CTL_ccc)

cellchat_Kim_scB16F10_B16F10_all <- identifyOverExpressedInteractions(cellchat_Kim_scB16F10_B16F10_all)
cellchat_Kim_scB16F10_B16F10_secreted <- identifyOverExpressedInteractions(cellchat_Kim_scB16F10_B16F10_secreted)
cellchat_Kim_scB16F10_B16F10_ECM <- identifyOverExpressedInteractions(cellchat_Kim_scB16F10_B16F10_ECM)
cellchat_Kim_scB16F10_B16F10_nps <- identifyOverExpressedInteractions(cellchat_Kim_scB16F10_B16F10_nps)
cellchat_Kim_scB16F10_B16F10_ccc <- identifyOverExpressedInteractions(cellchat_Kim_scB16F10_B16F10_ccc)

cellchat_Pryce_scC26_CTL_all <- identifyOverExpressedInteractions(cellchat_Pryce_scC26_CTL_all)
cellchat_Pryce_scC26_CTL_secreted <- identifyOverExpressedInteractions(cellchat_Pryce_scC26_CTL_secreted)
cellchat_Pryce_scC26_CTL_ECM <- identifyOverExpressedInteractions(cellchat_Pryce_scC26_CTL_ECM)
cellchat_Pryce_scC26_CTL_nps <- identifyOverExpressedInteractions(cellchat_Pryce_scC26_CTL_nps)
cellchat_Pryce_scC26_CTL_ccc <- identifyOverExpressedInteractions(cellchat_Pryce_scC26_CTL_ccc)

cellchat_Pryce_scC26_C26_all <- identifyOverExpressedInteractions(cellchat_Pryce_scC26_C26_all)
cellchat_Pryce_scC26_C26_secreted <- identifyOverExpressedInteractions(cellchat_Pryce_scC26_C26_secreted)
cellchat_Pryce_scC26_C26_ECM <- identifyOverExpressedInteractions(cellchat_Pryce_scC26_C26_ECM)
cellchat_Pryce_scC26_C26_nps <- identifyOverExpressedInteractions(cellchat_Pryce_scC26_C26_nps)
cellchat_Pryce_scC26_C26_ccc <- identifyOverExpressedInteractions(cellchat_Pryce_scC26_C26_ccc)

cellchat_Pryce_scKPP_CTL_all <- identifyOverExpressedInteractions(cellchat_Pryce_scKPP_CTL_all)
cellchat_Pryce_scKPP_CTL_secreted <- identifyOverExpressedInteractions(cellchat_Pryce_scKPP_CTL_secreted)
cellchat_Pryce_scKPP_CTL_ECM <- identifyOverExpressedInteractions(cellchat_Pryce_scKPP_CTL_ECM)
cellchat_Pryce_scKPP_CTL_nps <- identifyOverExpressedInteractions(cellchat_Pryce_scKPP_CTL_nps)
cellchat_Pryce_scKPP_CTL_ccc <- identifyOverExpressedInteractions(cellchat_Pryce_scKPP_CTL_ccc)

cellchat_Pryce_scKPP_KPP_all <- identifyOverExpressedInteractions(cellchat_Pryce_scKPP_KPP_all)
cellchat_Pryce_scKPP_KPP_secreted <- identifyOverExpressedInteractions(cellchat_Pryce_scKPP_KPP_secreted)
cellchat_Pryce_scKPP_KPP_ECM <- identifyOverExpressedInteractions(cellchat_Pryce_scKPP_KPP_ECM)
cellchat_Pryce_scKPP_KPP_nps <- identifyOverExpressedInteractions(cellchat_Pryce_scKPP_KPP_nps)
cellchat_Pryce_scKPP_KPP_ccc <- identifyOverExpressedInteractions(cellchat_Pryce_scKPP_KPP_ccc)

cellchat_Zhang_snKIC_CTL_all <- identifyOverExpressedInteractions(cellchat_Zhang_snKIC_CTL_all)
cellchat_Zhang_snKIC_CTL_secreted <- identifyOverExpressedInteractions(cellchat_Zhang_snKIC_CTL_secreted)
cellchat_Zhang_snKIC_CTL_ECM <- identifyOverExpressedInteractions(cellchat_Zhang_snKIC_CTL_ECM)
cellchat_Zhang_snKIC_CTL_nps <- identifyOverExpressedInteractions(cellchat_Zhang_snKIC_CTL_nps)
cellchat_Zhang_snKIC_CTL_ccc <- identifyOverExpressedInteractions(cellchat_Zhang_snKIC_CTL_ccc)

cellchat_Zhang_snKIC_KIC_all <- identifyOverExpressedInteractions(cellchat_Zhang_snKIC_KIC_all)
cellchat_Zhang_snKIC_KIC_secreted <- identifyOverExpressedInteractions(cellchat_Zhang_snKIC_KIC_secreted)
cellchat_Zhang_snKIC_KIC_ECM <- identifyOverExpressedInteractions(cellchat_Zhang_snKIC_KIC_ECM)
cellchat_Zhang_snKIC_KIC_nps <- identifyOverExpressedInteractions(cellchat_Zhang_snKIC_KIC_nps)
cellchat_Zhang_snKIC_KIC_ccc <- identifyOverExpressedInteractions(cellchat_Zhang_snKIC_KIC_ccc)
```



# Project gene expression data onto protein-protein interaction network

```{r, include=FALSE}
cellchat_Agca_snLLC_CTL_all <- projectData(cellchat_Agca_snLLC_CTL_all, PPI.mouse)
cellchat_Agca_snLLC_CTL_secreted <- projectData(cellchat_Agca_snLLC_CTL_secreted, PPI.mouse)
cellchat_Agca_snLLC_CTL_ECM <- projectData(cellchat_Agca_snLLC_CTL_ECM, PPI.mouse)
cellchat_Agca_snLLC_CTL_nps <- projectData(cellchat_Agca_snLLC_CTL_nps, PPI.mouse)
cellchat_Agca_snLLC_CTL_ccc <- projectData(cellchat_Agca_snLLC_CTL_ccc, PPI.mouse)

cellchat_Agca_snLLC_LLC_all <- projectData(cellchat_Agca_snLLC_LLC_all, PPI.mouse)
cellchat_Agca_snLLC_LLC_secreted <- projectData(cellchat_Agca_snLLC_LLC_secreted, PPI.mouse)
cellchat_Agca_snLLC_LLC_ECM <- projectData(cellchat_Agca_snLLC_LLC_ECM, PPI.mouse)
cellchat_Agca_snLLC_LLC_nps <- projectData(cellchat_Agca_snLLC_LLC_nps, PPI.mouse)
cellchat_Agca_snLLC_LLC_ccc <- projectData(cellchat_Agca_snLLC_LLC_ccc, PPI.mouse)

cellchat_Brown_scLLC_CTL_all <- projectData(cellchat_Brown_scLLC_CTL_all, PPI.mouse)
cellchat_Brown_scLLC_CTL_secreted <- projectData(cellchat_Brown_scLLC_CTL_secreted, PPI.mouse)
cellchat_Brown_scLLC_CTL_ECM <- projectData(cellchat_Brown_scLLC_CTL_ECM, PPI.mouse)
cellchat_Brown_scLLC_CTL_nps <- projectData(cellchat_Brown_scLLC_CTL_nps, PPI.mouse)
cellchat_Brown_scLLC_CTL_ccc <- projectData(cellchat_Brown_scLLC_CTL_ccc, PPI.mouse)

cellchat_Brown_scLLC_2w_all <- projectData(cellchat_Brown_scLLC_2w_all, PPI.mouse)
cellchat_Brown_scLLC_2w_secreted <- projectData(cellchat_Brown_scLLC_2w_secreted, PPI.mouse)
cellchat_Brown_scLLC_2w_ECM <- projectData(cellchat_Brown_scLLC_2w_ECM, PPI.mouse)
cellchat_Brown_scLLC_2w_nps <- projectData(cellchat_Brown_scLLC_2w_nps, PPI.mouse)
cellchat_Brown_scLLC_2w_ccc <- projectData(cellchat_Brown_scLLC_2w_ccc, PPI.mouse)

cellchat_Brown_scLLC_2.5w_all <- projectData(cellchat_Brown_scLLC_2.5w_all, PPI.mouse)
cellchat_Brown_scLLC_2.5w_secreted <- projectData(cellchat_Brown_scLLC_2.5w_secreted, PPI.mouse)
cellchat_Brown_scLLC_2.5w_ECM <- projectData(cellchat_Brown_scLLC_2.5w_ECM, PPI.mouse)
cellchat_Brown_scLLC_2.5w_nps <- projectData(cellchat_Brown_scLLC_2.5w_nps, PPI.mouse)
cellchat_Brown_scLLC_2.5w_ccc <- projectData(cellchat_Brown_scLLC_2.5w_ccc, PPI.mouse)

cellchat_Brown_scLLC_3.5w_all <- projectData(cellchat_Brown_scLLC_3.5w_all, PPI.mouse)
cellchat_Brown_scLLC_3.5w_secreted <- projectData(cellchat_Brown_scLLC_3.5w_secreted, PPI.mouse)
cellchat_Brown_scLLC_3.5w_ECM <- projectData(cellchat_Brown_scLLC_3.5w_ECM, PPI.mouse)
cellchat_Brown_scLLC_3.5w_nps <- projectData(cellchat_Brown_scLLC_3.5w_nps, PPI.mouse)
cellchat_Brown_scLLC_3.5w_ccc <- projectData(cellchat_Brown_scLLC_3.5w_ccc, PPI.mouse)

cellchat_Kim_scB16F10_CTL_all <- projectData(cellchat_Kim_scB16F10_CTL_all, PPI.mouse)
cellchat_Kim_scB16F10_CTL_secreted <- projectData(cellchat_Kim_scB16F10_CTL_secreted, PPI.mouse)
cellchat_Kim_scB16F10_CTL_ECM <- projectData(cellchat_Kim_scB16F10_CTL_ECM, PPI.mouse)
cellchat_Kim_scB16F10_CTL_nps <- projectData(cellchat_Kim_scB16F10_CTL_nps, PPI.mouse)
cellchat_Kim_scB16F10_CTL_ccc <- projectData(cellchat_Kim_scB16F10_CTL_ccc, PPI.mouse)

cellchat_Kim_scB16F10_B16F10_all <- projectData(cellchat_Kim_scB16F10_B16F10_all, PPI.mouse)
cellchat_Kim_scB16F10_B16F10_secreted <- projectData(cellchat_Kim_scB16F10_B16F10_secreted, PPI.mouse)
cellchat_Kim_scB16F10_B16F10_ECM <- projectData(cellchat_Kim_scB16F10_B16F10_ECM, PPI.mouse)
cellchat_Kim_scB16F10_B16F10_nps <- projectData(cellchat_Kim_scB16F10_B16F10_nps, PPI.mouse)
cellchat_Kim_scB16F10_B16F10_ccc <- projectData(cellchat_Kim_scB16F10_B16F10_ccc, PPI.mouse)

cellchat_Pryce_scC26_CTL_all <- projectData(cellchat_Pryce_scC26_CTL_all, PPI.mouse)
cellchat_Pryce_scC26_CTL_secreted <- projectData(cellchat_Pryce_scC26_CTL_secreted, PPI.mouse)
cellchat_Pryce_scC26_CTL_ECM <- projectData(cellchat_Pryce_scC26_CTL_ECM, PPI.mouse)
cellchat_Pryce_scC26_CTL_nps <- projectData(cellchat_Pryce_scC26_CTL_nps, PPI.mouse)
cellchat_Pryce_scC26_CTL_ccc <- projectData(cellchat_Pryce_scC26_CTL_ccc, PPI.mouse)

cellchat_Pryce_scC26_C26_all <- projectData(cellchat_Pryce_scC26_C26_all, PPI.mouse)
cellchat_Pryce_scC26_C26_secreted <- projectData(cellchat_Pryce_scC26_C26_secreted, PPI.mouse)
cellchat_Pryce_scC26_C26_ECM <- projectData(cellchat_Pryce_scC26_C26_ECM, PPI.mouse)
cellchat_Pryce_scC26_C26_nps <- projectData(cellchat_Pryce_scC26_C26_nps, PPI.mouse)
cellchat_Pryce_scC26_C26_ccc <- projectData(cellchat_Pryce_scC26_C26_ccc, PPI.mouse)

cellchat_Pryce_scKPP_CTL_all <- projectData(cellchat_Pryce_scKPP_CTL_all, PPI.mouse)
cellchat_Pryce_scKPP_CTL_secreted <- projectData(cellchat_Pryce_scKPP_CTL_secreted, PPI.mouse)
cellchat_Pryce_scKPP_CTL_ECM <- projectData(cellchat_Pryce_scKPP_CTL_ECM, PPI.mouse)
cellchat_Pryce_scKPP_CTL_nps <- projectData(cellchat_Pryce_scKPP_CTL_nps, PPI.mouse)
cellchat_Pryce_scKPP_CTL_ccc <- projectData(cellchat_Pryce_scKPP_CTL_ccc, PPI.mouse)

cellchat_Pryce_scKPP_KPP_all <- projectData(cellchat_Pryce_scKPP_KPP_all, PPI.mouse)
cellchat_Pryce_scKPP_KPP_secreted <- projectData(cellchat_Pryce_scKPP_KPP_secreted, PPI.mouse)
cellchat_Pryce_scKPP_KPP_ECM <- projectData(cellchat_Pryce_scKPP_KPP_ECM, PPI.mouse)
cellchat_Pryce_scKPP_KPP_nps <- projectData(cellchat_Pryce_scKPP_KPP_nps, PPI.mouse)
cellchat_Pryce_scKPP_KPP_ccc <- projectData(cellchat_Pryce_scKPP_KPP_ccc, PPI.mouse)

cellchat_Zhang_snKIC_CTL_all <- projectData(cellchat_Zhang_snKIC_CTL_all, PPI.mouse)
cellchat_Zhang_snKIC_CTL_secreted <- projectData(cellchat_Zhang_snKIC_CTL_secreted, PPI.mouse)
cellchat_Zhang_snKIC_CTL_ECM <- projectData(cellchat_Zhang_snKIC_CTL_ECM, PPI.mouse)
cellchat_Zhang_snKIC_CTL_nps <- projectData(cellchat_Zhang_snKIC_CTL_nps, PPI.mouse)
cellchat_Zhang_snKIC_CTL_ccc <- projectData(cellchat_Zhang_snKIC_CTL_ccc, PPI.mouse)

cellchat_Zhang_snKIC_KIC_all <- projectData(cellchat_Zhang_snKIC_KIC_all, PPI.mouse)
cellchat_Zhang_snKIC_KIC_secreted <- projectData(cellchat_Zhang_snKIC_KIC_secreted, PPI.mouse)
cellchat_Zhang_snKIC_KIC_ECM <- projectData(cellchat_Zhang_snKIC_KIC_ECM, PPI.mouse)
cellchat_Zhang_snKIC_KIC_nps <- projectData(cellchat_Zhang_snKIC_KIC_nps, PPI.mouse)
cellchat_Zhang_snKIC_KIC_ccc <- projectData(cellchat_Zhang_snKIC_KIC_ccc, PPI.mouse)
```



# Remove unused levels

```{r, include=FALSE}
# Agca_snLLC_CTL
cellchat_Agca_snLLC_CTL_all@idents <- droplevels(cellchat_Agca_snLLC_CTL_all@idents, exclude = setdiff(levels(cellchat_Agca_snLLC_CTL_meta$group), unique(cellchat_Agca_snLLC_CTL_meta$group)))
cellchat_Agca_snLLC_CTL_secreted@idents <- droplevels(cellchat_Agca_snLLC_CTL_secreted@idents, exclude = setdiff(levels(cellchat_Agca_snLLC_CTL_meta$group), unique(cellchat_Agca_snLLC_CTL_meta$group)))
cellchat_Agca_snLLC_CTL_ECM@idents <- droplevels(cellchat_Agca_snLLC_CTL_ECM@idents, exclude = setdiff(levels(cellchat_Agca_snLLC_CTL_meta$group), unique(cellchat_Agca_snLLC_CTL_meta$group)))
cellchat_Agca_snLLC_CTL_nps@idents <- droplevels(cellchat_Agca_snLLC_CTL_nps@idents, exclude = setdiff(levels(cellchat_Agca_snLLC_CTL_meta$group), unique(cellchat_Agca_snLLC_CTL_meta$group)))
cellchat_Agca_snLLC_CTL_ccc@idents <- droplevels(cellchat_Agca_snLLC_CTL_ccc@idents, exclude = setdiff(levels(cellchat_Agca_snLLC_CTL_meta$group), unique(cellchat_Agca_snLLC_CTL_meta$group)))

# Agca_snLLC_LLC
cellchat_Agca_snLLC_LLC_all@idents <- droplevels(cellchat_Agca_snLLC_LLC_all@idents, exclude = setdiff(levels(cellchat_Agca_snLLC_LLC_meta$group), unique(cellchat_Agca_snLLC_LLC_meta$group)))
cellchat_Agca_snLLC_LLC_secreted@idents <- droplevels(cellchat_Agca_snLLC_LLC_secreted@idents, exclude = setdiff(levels(cellchat_Agca_snLLC_LLC_meta$group), unique(cellchat_Agca_snLLC_LLC_meta$group)))
cellchat_Agca_snLLC_LLC_ECM@idents <- droplevels(cellchat_Agca_snLLC_LLC_ECM@idents, exclude = setdiff(levels(cellchat_Agca_snLLC_LLC_meta$group), unique(cellchat_Agca_snLLC_LLC_meta$group)))
cellchat_Agca_snLLC_LLC_nps@idents <- droplevels(cellchat_Agca_snLLC_LLC_nps@idents, exclude = setdiff(levels(cellchat_Agca_snLLC_LLC_meta$group), unique(cellchat_Agca_snLLC_LLC_meta$group)))
cellchat_Agca_snLLC_LLC_ccc@idents <- droplevels(cellchat_Agca_snLLC_LLC_ccc@idents, exclude = setdiff(levels(cellchat_Agca_snLLC_LLC_meta$group), unique(cellchat_Agca_snLLC_LLC_meta$group)))

# Brown_scLLC_CTL
cellchat_Brown_scLLC_CTL_all@idents <- droplevels(cellchat_Brown_scLLC_CTL_all@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_CTL_meta$group), unique(cellchat_Brown_scLLC_CTL_meta$group)))
cellchat_Brown_scLLC_CTL_secreted@idents <- droplevels(cellchat_Brown_scLLC_CTL_secreted@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_CTL_meta$group), unique(cellchat_Brown_scLLC_CTL_meta$group)))
cellchat_Brown_scLLC_CTL_ECM@idents <- droplevels(cellchat_Brown_scLLC_CTL_ECM@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_CTL_meta$group), unique(cellchat_Brown_scLLC_CTL_meta$group)))
cellchat_Brown_scLLC_CTL_nps@idents <- droplevels(cellchat_Brown_scLLC_CTL_nps@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_CTL_meta$group), unique(cellchat_Brown_scLLC_CTL_meta$group)))
cellchat_Brown_scLLC_CTL_ccc@idents <- droplevels(cellchat_Brown_scLLC_CTL_ccc@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_CTL_meta$group), unique(cellchat_Brown_scLLC_CTL_meta$group)))

# Brown_scLLC_2w
cellchat_Brown_scLLC_2w_all@idents <- droplevels(cellchat_Brown_scLLC_2w_all@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_2w_meta$group), unique(cellchat_Brown_scLLC_2w_meta$group)))
cellchat_Brown_scLLC_2w_secreted@idents <- droplevels(cellchat_Brown_scLLC_2w_secreted@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_2w_meta$group), unique(cellchat_Brown_scLLC_2w_meta$group)))
cellchat_Brown_scLLC_2w_ECM@idents <- droplevels(cellchat_Brown_scLLC_2w_ECM@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_2w_meta$group), unique(cellchat_Brown_scLLC_2w_meta$group)))
cellchat_Brown_scLLC_2w_nps@idents <- droplevels(cellchat_Brown_scLLC_2w_nps@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_2w_meta$group), unique(cellchat_Brown_scLLC_2w_meta$group)))
cellchat_Brown_scLLC_2w_ccc@idents <- droplevels(cellchat_Brown_scLLC_2w_ccc@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_2w_meta$group), unique(cellchat_Brown_scLLC_2w_meta$group)))

# Brown_scLLC_2.5w
cellchat_Brown_scLLC_2.5w_all@idents <- droplevels(cellchat_Brown_scLLC_2.5w_all@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_2.5w_meta$group), unique(cellchat_Brown_scLLC_2.5w_meta$group)))
cellchat_Brown_scLLC_2.5w_secreted@idents <- droplevels(cellchat_Brown_scLLC_2.5w_secreted@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_2.5w_meta$group), unique(cellchat_Brown_scLLC_2.5w_meta$group)))
cellchat_Brown_scLLC_2.5w_ECM@idents <- droplevels(cellchat_Brown_scLLC_2.5w_ECM@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_2.5w_meta$group), unique(cellchat_Brown_scLLC_2.5w_meta$group)))
cellchat_Brown_scLLC_2.5w_nps@idents <- droplevels(cellchat_Brown_scLLC_2.5w_nps@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_2.5w_meta$group), unique(cellchat_Brown_scLLC_2.5w_meta$group)))
cellchat_Brown_scLLC_2.5w_ccc@idents <- droplevels(cellchat_Brown_scLLC_2.5w_ccc@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_2.5w_meta$group), unique(cellchat_Brown_scLLC_2.5w_meta$group)))

# Brown_scLLC_3.5w
cellchat_Brown_scLLC_3.5w_all@idents <- droplevels(cellchat_Brown_scLLC_3.5w_all@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_3.5w_meta$group), unique(cellchat_Brown_scLLC_3.5w_meta$group)))
cellchat_Brown_scLLC_3.5w_secreted@idents <- droplevels(cellchat_Brown_scLLC_3.5w_secreted@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_3.5w_meta$group), unique(cellchat_Brown_scLLC_3.5w_meta$group)))
cellchat_Brown_scLLC_3.5w_ECM@idents <- droplevels(cellchat_Brown_scLLC_3.5w_ECM@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_3.5w_meta$group), unique(cellchat_Brown_scLLC_3.5w_meta$group)))
cellchat_Brown_scLLC_3.5w_nps@idents <- droplevels(cellchat_Brown_scLLC_3.5w_nps@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_3.5w_meta$group), unique(cellchat_Brown_scLLC_3.5w_meta$group)))
cellchat_Brown_scLLC_3.5w_ccc@idents <- droplevels(cellchat_Brown_scLLC_3.5w_ccc@idents, exclude = setdiff(levels(cellchat_Brown_scLLC_3.5w_meta$group), unique(cellchat_Brown_scLLC_3.5w_meta$group)))

# Kim_scB16F10_CTL
cellchat_Kim_scB16F10_CTL_all@idents <- droplevels(cellchat_Kim_scB16F10_CTL_all@idents, exclude = setdiff(levels(cellchat_Kim_scB16F10_CTL_meta$group), unique(cellchat_Kim_scB16F10_CTL_meta$group)))
cellchat_Kim_scB16F10_CTL_secreted@idents <- droplevels(cellchat_Kim_scB16F10_CTL_secreted@idents, exclude = setdiff(levels(cellchat_Kim_scB16F10_CTL_meta$group), unique(cellchat_Kim_scB16F10_CTL_meta$group)))
cellchat_Kim_scB16F10_CTL_ECM@idents <- droplevels(cellchat_Kim_scB16F10_CTL_ECM@idents, exclude = setdiff(levels(cellchat_Kim_scB16F10_CTL_meta$group), unique(cellchat_Kim_scB16F10_CTL_meta$group)))
cellchat_Kim_scB16F10_CTL_nps@idents <- droplevels(cellchat_Kim_scB16F10_CTL_nps@idents, exclude = setdiff(levels(cellchat_Kim_scB16F10_CTL_meta$group), unique(cellchat_Kim_scB16F10_CTL_meta$group)))
cellchat_Kim_scB16F10_CTL_ccc@idents <- droplevels(cellchat_Kim_scB16F10_CTL_ccc@idents, exclude = setdiff(levels(cellchat_Kim_scB16F10_CTL_meta$group), unique(cellchat_Kim_scB16F10_CTL_meta$group)))

# Kim_scB16F10_B16F10
cellchat_Kim_scB16F10_B16F10_all@idents <- droplevels(cellchat_Kim_scB16F10_B16F10_all@idents, exclude = setdiff(levels(cellchat_Kim_scB16F10_B16F10_meta$group), unique(cellchat_Kim_scB16F10_B16F10_meta$group)))
cellchat_Kim_scB16F10_B16F10_secreted@idents <- droplevels(cellchat_Kim_scB16F10_B16F10_secreted@idents, exclude = setdiff(levels(cellchat_Kim_scB16F10_B16F10_meta$group), unique(cellchat_Kim_scB16F10_B16F10_meta$group)))
cellchat_Kim_scB16F10_B16F10_ECM@idents <- droplevels(cellchat_Kim_scB16F10_B16F10_ECM@idents, exclude = setdiff(levels(cellchat_Kim_scB16F10_B16F10_meta$group), unique(cellchat_Kim_scB16F10_B16F10_meta$group)))
cellchat_Kim_scB16F10_B16F10_nps@idents <- droplevels(cellchat_Kim_scB16F10_B16F10_nps@idents, exclude = setdiff(levels(cellchat_Kim_scB16F10_B16F10_meta$group), unique(cellchat_Kim_scB16F10_B16F10_meta$group)))
cellchat_Kim_scB16F10_B16F10_ccc@idents <- droplevels(cellchat_Kim_scB16F10_B16F10_ccc@idents, exclude = setdiff(levels(cellchat_Kim_scB16F10_B16F10_meta$group), unique(cellchat_Kim_scB16F10_B16F10_meta$group)))

# Pryce_scC26_CTL
cellchat_Pryce_scC26_CTL_all@idents <- droplevels(cellchat_Pryce_scC26_CTL_all@idents, exclude = setdiff(levels(cellchat_Pryce_scC26_CTL_meta$group), unique(cellchat_Pryce_scC26_CTL_meta$group)))
cellchat_Pryce_scC26_CTL_secreted@idents <- droplevels(cellchat_Pryce_scC26_CTL_secreted@idents, exclude = setdiff(levels(cellchat_Pryce_scC26_CTL_meta$group), unique(cellchat_Pryce_scC26_CTL_meta$group)))
cellchat_Pryce_scC26_CTL_ECM@idents <- droplevels(cellchat_Pryce_scC26_CTL_ECM@idents, exclude = setdiff(levels(cellchat_Pryce_scC26_CTL_meta$group), unique(cellchat_Pryce_scC26_CTL_meta$group)))
cellchat_Pryce_scC26_CTL_nps@idents <- droplevels(cellchat_Pryce_scC26_CTL_nps@idents, exclude = setdiff(levels(cellchat_Pryce_scC26_CTL_meta$group), unique(cellchat_Pryce_scC26_CTL_meta$group)))
cellchat_Pryce_scC26_CTL_ccc@idents <- droplevels(cellchat_Pryce_scC26_CTL_ccc@idents, exclude = setdiff(levels(cellchat_Pryce_scC26_CTL_meta$group), unique(cellchat_Pryce_scC26_CTL_meta$group)))

# Pryce_scC26_C26
cellchat_Pryce_scC26_C26_all@idents <- droplevels(cellchat_Pryce_scC26_C26_all@idents, exclude = setdiff(levels(cellchat_Pryce_scC26_C26_meta$group), unique(cellchat_Pryce_scC26_C26_meta$group)))
cellchat_Pryce_scC26_C26_secreted@idents <- droplevels(cellchat_Pryce_scC26_C26_secreted@idents, exclude = setdiff(levels(cellchat_Pryce_scC26_C26_meta$group), unique(cellchat_Pryce_scC26_C26_meta$group)))
cellchat_Pryce_scC26_C26_ECM@idents <- droplevels(cellchat_Pryce_scC26_C26_ECM@idents, exclude = setdiff(levels(cellchat_Pryce_scC26_C26_meta$group), unique(cellchat_Pryce_scC26_C26_meta$group)))
cellchat_Pryce_scC26_C26_nps@idents <- droplevels(cellchat_Pryce_scC26_C26_nps@idents, exclude = setdiff(levels(cellchat_Pryce_scC26_C26_meta$group), unique(cellchat_Pryce_scC26_C26_meta$group)))
cellchat_Pryce_scC26_C26_ccc@idents <- droplevels(cellchat_Pryce_scC26_C26_ccc@idents, exclude = setdiff(levels(cellchat_Pryce_scC26_C26_meta$group), unique(cellchat_Pryce_scC26_C26_meta$group)))

# Pryce_scKPP_CTL
cellchat_Pryce_scKPP_CTL_all@idents <- droplevels(cellchat_Pryce_scKPP_CTL_all@idents, exclude = setdiff(levels(cellchat_Pryce_scKPP_CTL_meta$group), unique(cellchat_Pryce_scKPP_CTL_meta$group)))
cellchat_Pryce_scKPP_CTL_secreted@idents <- droplevels(cellchat_Pryce_scKPP_CTL_secreted@idents, exclude = setdiff(levels(cellchat_Pryce_scKPP_CTL_meta$group), unique(cellchat_Pryce_scKPP_CTL_meta$group)))
cellchat_Pryce_scKPP_CTL_ECM@idents <- droplevels(cellchat_Pryce_scKPP_CTL_ECM@idents, exclude = setdiff(levels(cellchat_Pryce_scKPP_CTL_meta$group), unique(cellchat_Pryce_scKPP_CTL_meta$group)))
cellchat_Pryce_scKPP_CTL_nps@idents <- droplevels(cellchat_Pryce_scKPP_CTL_nps@idents, exclude = setdiff(levels(cellchat_Pryce_scKPP_CTL_meta$group), unique(cellchat_Pryce_scKPP_CTL_meta$group)))
cellchat_Pryce_scKPP_CTL_ccc@idents <- droplevels(cellchat_Pryce_scKPP_CTL_ccc@idents, exclude = setdiff(levels(cellchat_Pryce_scKPP_CTL_meta$group), unique(cellchat_Pryce_scKPP_CTL_meta$group)))

# Pryce_scKPP_KPP
cellchat_Pryce_scKPP_KPP_all@idents <- droplevels(cellchat_Pryce_scKPP_KPP_all@idents, exclude = setdiff(levels(cellchat_Pryce_scKPP_KPP_meta$group), unique(cellchat_Pryce_scKPP_KPP_meta$group)))
cellchat_Pryce_scKPP_KPP_secreted@idents <- droplevels(cellchat_Pryce_scKPP_KPP_secreted@idents, exclude = setdiff(levels(cellchat_Pryce_scKPP_KPP_meta$group), unique(cellchat_Pryce_scKPP_KPP_meta$group)))
cellchat_Pryce_scKPP_KPP_ECM@idents <- droplevels(cellchat_Pryce_scKPP_KPP_ECM@idents, exclude = setdiff(levels(cellchat_Pryce_scKPP_KPP_meta$group), unique(cellchat_Pryce_scKPP_KPP_meta$group)))
cellchat_Pryce_scKPP_KPP_nps@idents <- droplevels(cellchat_Pryce_scKPP_KPP_nps@idents, exclude = setdiff(levels(cellchat_Pryce_scKPP_KPP_meta$group), unique(cellchat_Pryce_scKPP_KPP_meta$group)))
cellchat_Pryce_scKPP_KPP_ccc@idents <- droplevels(cellchat_Pryce_scKPP_KPP_ccc@idents, exclude = setdiff(levels(cellchat_Pryce_scKPP_KPP_meta$group), unique(cellchat_Pryce_scKPP_KPP_meta$group)))

# Zhang_snKIC_CTL
cellchat_Zhang_snKIC_CTL_all@idents <- droplevels(cellchat_Zhang_snKIC_CTL_all@idents, exclude = setdiff(levels(cellchat_Zhang_snKIC_CTL_meta$group), unique(cellchat_Zhang_snKIC_CTL_meta$group)))
cellchat_Zhang_snKIC_CTL_secreted@idents <- droplevels(cellchat_Zhang_snKIC_CTL_secreted@idents, exclude = setdiff(levels(cellchat_Zhang_snKIC_CTL_meta$group), unique(cellchat_Zhang_snKIC_CTL_meta$group)))
cellchat_Zhang_snKIC_CTL_ECM@idents <- droplevels(cellchat_Zhang_snKIC_CTL_ECM@idents, exclude = setdiff(levels(cellchat_Zhang_snKIC_CTL_meta$group), unique(cellchat_Zhang_snKIC_CTL_meta$group)))
cellchat_Zhang_snKIC_CTL_nps@idents <- droplevels(cellchat_Zhang_snKIC_CTL_nps@idents, exclude = setdiff(levels(cellchat_Zhang_snKIC_CTL_meta$group), unique(cellchat_Zhang_snKIC_CTL_meta$group)))
cellchat_Zhang_snKIC_CTL_ccc@idents <- droplevels(cellchat_Zhang_snKIC_CTL_ccc@idents, exclude = setdiff(levels(cellchat_Zhang_snKIC_CTL_meta$group), unique(cellchat_Zhang_snKIC_CTL_meta$group)))

# Zhang_snKIC_KIC
cellchat_Zhang_snKIC_KIC_all@idents <- droplevels(cellchat_Zhang_snKIC_KIC_all@idents, exclude = setdiff(levels(cellchat_Zhang_snKIC_KIC_meta$group), unique(cellchat_Zhang_snKIC_KIC_meta$group)))
cellchat_Zhang_snKIC_KIC_secreted@idents <- droplevels(cellchat_Zhang_snKIC_KIC_secreted@idents, exclude = setdiff(levels(cellchat_Zhang_snKIC_KIC_meta$group), unique(cellchat_Zhang_snKIC_KIC_meta$group)))
cellchat_Zhang_snKIC_KIC_ECM@idents <- droplevels(cellchat_Zhang_snKIC_KIC_ECM@idents, exclude = setdiff(levels(cellchat_Zhang_snKIC_KIC_meta$group), unique(cellchat_Zhang_snKIC_KIC_meta$group)))
cellchat_Zhang_snKIC_KIC_nps@idents <- droplevels(cellchat_Zhang_snKIC_KIC_nps@idents, exclude = setdiff(levels(cellchat_Zhang_snKIC_KIC_meta$group), unique(cellchat_Zhang_snKIC_KIC_meta$group)))
cellchat_Zhang_snKIC_KIC_ccc@idents <- droplevels(cellchat_Zhang_snKIC_KIC_ccc@idents, exclude = setdiff(levels(cellchat_Zhang_snKIC_KIC_meta$group), unique(cellchat_Zhang_snKIC_KIC_meta$group)))
```



# Identify communication probabilities

```{r, include=FALSE}
# Agca_snLLC_CTL
cellchat_Agca_snLLC_CTL_all <- computeCommunProb(cellchat_Agca_snLLC_CTL_all)
cellchat_Agca_snLLC_CTL_all <- computeCommunProbPathway(cellchat_Agca_snLLC_CTL_all)
cellchat_Agca_snLLC_CTL_all <- aggregateNet(cellchat_Agca_snLLC_CTL_all)
cellchat_Agca_snLLC_CTL_all <- netAnalysis_computeCentrality(cellchat_Agca_snLLC_CTL_all, slot.name = "netP")

cellchat_Agca_snLLC_CTL_secreted <- computeCommunProb(cellchat_Agca_snLLC_CTL_secreted)
cellchat_Agca_snLLC_CTL_secreted <- computeCommunProbPathway(cellchat_Agca_snLLC_CTL_secreted)
cellchat_Agca_snLLC_CTL_secreted <- aggregateNet(cellchat_Agca_snLLC_CTL_secreted)
cellchat_Agca_snLLC_CTL_secreted <- netAnalysis_computeCentrality(cellchat_Agca_snLLC_CTL_secreted, slot.name = "netP")

cellchat_Agca_snLLC_CTL_ECM <- computeCommunProb(cellchat_Agca_snLLC_CTL_ECM)
cellchat_Agca_snLLC_CTL_ECM <- computeCommunProbPathway(cellchat_Agca_snLLC_CTL_ECM)
cellchat_Agca_snLLC_CTL_ECM <- aggregateNet(cellchat_Agca_snLLC_CTL_ECM)
cellchat_Agca_snLLC_CTL_ECM <- netAnalysis_computeCentrality(cellchat_Agca_snLLC_CTL_ECM, slot.name = "netP")

cellchat_Agca_snLLC_CTL_nps <- computeCommunProb(cellchat_Agca_snLLC_CTL_nps)
cellchat_Agca_snLLC_CTL_nps <- computeCommunProbPathway(cellchat_Agca_snLLC_CTL_nps)
cellchat_Agca_snLLC_CTL_nps <- aggregateNet(cellchat_Agca_snLLC_CTL_nps)
cellchat_Agca_snLLC_CTL_nps <- netAnalysis_computeCentrality(cellchat_Agca_snLLC_CTL_nps, slot.name = "netP")

cellchat_Agca_snLLC_CTL_ccc <- computeCommunProb(cellchat_Agca_snLLC_CTL_ccc)
cellchat_Agca_snLLC_CTL_ccc <- computeCommunProbPathway(cellchat_Agca_snLLC_CTL_ccc)
cellchat_Agca_snLLC_CTL_ccc <- aggregateNet(cellchat_Agca_snLLC_CTL_ccc)
cellchat_Agca_snLLC_CTL_ccc <- netAnalysis_computeCentrality(cellchat_Agca_snLLC_CTL_ccc, slot.name = "netP")

# Agca_snLLC_LLC
cellchat_Agca_snLLC_LLC_all <- computeCommunProb(cellchat_Agca_snLLC_LLC_all)
cellchat_Agca_snLLC_LLC_all <- computeCommunProbPathway(cellchat_Agca_snLLC_LLC_all)
cellchat_Agca_snLLC_LLC_all <- aggregateNet(cellchat_Agca_snLLC_LLC_all)
cellchat_Agca_snLLC_LLC_all <- netAnalysis_computeCentrality(cellchat_Agca_snLLC_LLC_all, slot.name = "netP")

cellchat_Agca_snLLC_LLC_secreted <- computeCommunProb(cellchat_Agca_snLLC_LLC_secreted)
cellchat_Agca_snLLC_LLC_secreted <- computeCommunProbPathway(cellchat_Agca_snLLC_LLC_secreted)
cellchat_Agca_snLLC_LLC_secreted <- aggregateNet(cellchat_Agca_snLLC_LLC_secreted)
cellchat_Agca_snLLC_LLC_secreted <- netAnalysis_computeCentrality(cellchat_Agca_snLLC_LLC_secreted, slot.name = "netP")

cellchat_Agca_snLLC_LLC_ECM <- computeCommunProb(cellchat_Agca_snLLC_LLC_ECM)
cellchat_Agca_snLLC_LLC_ECM <- computeCommunProbPathway(cellchat_Agca_snLLC_LLC_ECM)
cellchat_Agca_snLLC_LLC_ECM <- aggregateNet(cellchat_Agca_snLLC_LLC_ECM)
cellchat_Agca_snLLC_LLC_ECM <- netAnalysis_computeCentrality(cellchat_Agca_snLLC_LLC_ECM, slot.name = "netP")

cellchat_Agca_snLLC_LLC_nps <- computeCommunProb(cellchat_Agca_snLLC_LLC_nps)
cellchat_Agca_snLLC_LLC_nps <- computeCommunProbPathway(cellchat_Agca_snLLC_LLC_nps)
cellchat_Agca_snLLC_LLC_nps <- aggregateNet(cellchat_Agca_snLLC_LLC_nps)
cellchat_Agca_snLLC_LLC_nps <- netAnalysis_computeCentrality(cellchat_Agca_snLLC_LLC_nps, slot.name = "netP")

cellchat_Agca_snLLC_LLC_ccc <- computeCommunProb(cellchat_Agca_snLLC_LLC_ccc)
cellchat_Agca_snLLC_LLC_ccc <- computeCommunProbPathway(cellchat_Agca_snLLC_LLC_ccc)
cellchat_Agca_snLLC_LLC_ccc <- aggregateNet(cellchat_Agca_snLLC_LLC_ccc)
cellchat_Agca_snLLC_LLC_ccc <- netAnalysis_computeCentrality(cellchat_Agca_snLLC_LLC_ccc, slot.name = "netP")

# Brown_scLLC_CTL
cellchat_Brown_scLLC_CTL_all <- computeCommunProb(cellchat_Brown_scLLC_CTL_all)
cellchat_Brown_scLLC_CTL_all <- computeCommunProbPathway(cellchat_Brown_scLLC_CTL_all)
cellchat_Brown_scLLC_CTL_all <- aggregateNet(cellchat_Brown_scLLC_CTL_all)
cellchat_Brown_scLLC_CTL_all <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_CTL_all, slot.name = "netP")

cellchat_Brown_scLLC_CTL_secreted <- computeCommunProb(cellchat_Brown_scLLC_CTL_secreted)
cellchat_Brown_scLLC_CTL_secreted <- computeCommunProbPathway(cellchat_Brown_scLLC_CTL_secreted)
cellchat_Brown_scLLC_CTL_secreted <- aggregateNet(cellchat_Brown_scLLC_CTL_secreted)
cellchat_Brown_scLLC_CTL_secreted <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_CTL_secreted, slot.name = "netP")

cellchat_Brown_scLLC_CTL_ECM <- computeCommunProb(cellchat_Brown_scLLC_CTL_ECM)
cellchat_Brown_scLLC_CTL_ECM <- computeCommunProbPathway(cellchat_Brown_scLLC_CTL_ECM)
cellchat_Brown_scLLC_CTL_ECM <- aggregateNet(cellchat_Brown_scLLC_CTL_ECM)
cellchat_Brown_scLLC_CTL_ECM <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_CTL_ECM, slot.name = "netP")

cellchat_Brown_scLLC_CTL_nps <- computeCommunProb(cellchat_Brown_scLLC_CTL_nps)
cellchat_Brown_scLLC_CTL_nps <- computeCommunProbPathway(cellchat_Brown_scLLC_CTL_nps)
cellchat_Brown_scLLC_CTL_nps <- aggregateNet(cellchat_Brown_scLLC_CTL_nps)
cellchat_Brown_scLLC_CTL_nps <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_CTL_nps, slot.name = "netP")

cellchat_Brown_scLLC_CTL_ccc <- computeCommunProb(cellchat_Brown_scLLC_CTL_ccc)
cellchat_Brown_scLLC_CTL_ccc <- computeCommunProbPathway(cellchat_Brown_scLLC_CTL_ccc)
cellchat_Brown_scLLC_CTL_ccc <- aggregateNet(cellchat_Brown_scLLC_CTL_ccc)
cellchat_Brown_scLLC_CTL_ccc <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_CTL_ccc, slot.name = "netP")

# Brown_scLLC_2w
cellchat_Brown_scLLC_2w_all <- computeCommunProb(cellchat_Brown_scLLC_2w_all)
cellchat_Brown_scLLC_2w_all <- computeCommunProbPathway(cellchat_Brown_scLLC_2w_all)
cellchat_Brown_scLLC_2w_all <- aggregateNet(cellchat_Brown_scLLC_2w_all)
cellchat_Brown_scLLC_2w_all <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_2w_all, slot.name = "netP")

cellchat_Brown_scLLC_2w_secreted <- computeCommunProb(cellchat_Brown_scLLC_2w_secreted)
cellchat_Brown_scLLC_2w_secreted <- computeCommunProbPathway(cellchat_Brown_scLLC_2w_secreted)
cellchat_Brown_scLLC_2w_secreted <- aggregateNet(cellchat_Brown_scLLC_2w_secreted)
cellchat_Brown_scLLC_2w_secreted <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_2w_secreted, slot.name = "netP")

# Brown_scLLC_2w_ECM
cellchat_Brown_scLLC_2w_ECM <- computeCommunProb(cellchat_Brown_scLLC_2w_ECM)
cellchat_Brown_scLLC_2w_ECM <- computeCommunProbPathway(cellchat_Brown_scLLC_2w_ECM)
cellchat_Brown_scLLC_2w_ECM <- aggregateNet(cellchat_Brown_scLLC_2w_ECM)
cellchat_Brown_scLLC_2w_ECM <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_2w_ECM, slot.name = "netP")

# Brown_scLLC_2w_nps
cellchat_Brown_scLLC_2w_nps <- computeCommunProb(cellchat_Brown_scLLC_2w_nps)
cellchat_Brown_scLLC_2w_nps <- computeCommunProbPathway(cellchat_Brown_scLLC_2w_nps)
cellchat_Brown_scLLC_2w_nps <- aggregateNet(cellchat_Brown_scLLC_2w_nps)
cellchat_Brown_scLLC_2w_nps <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_2w_nps, slot.name = "netP")

# Brown_scLLC_2w_ccc
cellchat_Brown_scLLC_2w_ccc <- computeCommunProb(cellchat_Brown_scLLC_2w_ccc)
cellchat_Brown_scLLC_2w_ccc <- computeCommunProbPathway(cellchat_Brown_scLLC_2w_ccc)
cellchat_Brown_scLLC_2w_ccc <- aggregateNet(cellchat_Brown_scLLC_2w_ccc)
cellchat_Brown_scLLC_2w_ccc <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_2w_ccc, slot.name = "netP")

# Brown_scLLC_2.5w
cellchat_Brown_scLLC_2.5w_all <- computeCommunProb(cellchat_Brown_scLLC_2.5w_all)
cellchat_Brown_scLLC_2.5w_all <- computeCommunProbPathway(cellchat_Brown_scLLC_2.5w_all)
cellchat_Brown_scLLC_2.5w_all <- aggregateNet(cellchat_Brown_scLLC_2.5w_all)
cellchat_Brown_scLLC_2.5w_all <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_2.5w_all, slot.name = "netP")

cellchat_Brown_scLLC_2.5w_secreted <- computeCommunProb(cellchat_Brown_scLLC_2.5w_secreted)
cellchat_Brown_scLLC_2.5w_secreted <- computeCommunProbPathway(cellchat_Brown_scLLC_2.5w_secreted)
cellchat_Brown_scLLC_2.5w_secreted <- aggregateNet(cellchat_Brown_scLLC_2.5w_secreted)
cellchat_Brown_scLLC_2.5w_secreted <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_2.5w_secreted, slot.name = "netP")

cellchat_Brown_scLLC_2.5w_ECM <- computeCommunProb(cellchat_Brown_scLLC_2.5w_ECM)
cellchat_Brown_scLLC_2.5w_ECM <- computeCommunProbPathway(cellchat_Brown_scLLC_2.5w_ECM)
cellchat_Brown_scLLC_2.5w_ECM <- aggregateNet(cellchat_Brown_scLLC_2.5w_ECM)
cellchat_Brown_scLLC_2.5w_ECM <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_2.5w_ECM, slot.name = "netP")

cellchat_Brown_scLLC_2.5w_nps <- computeCommunProb(cellchat_Brown_scLLC_2.5w_nps)
cellchat_Brown_scLLC_2.5w_nps <- computeCommunProbPathway(cellchat_Brown_scLLC_2.5w_nps)
cellchat_Brown_scLLC_2.5w_nps <- aggregateNet(cellchat_Brown_scLLC_2.5w_nps)
cellchat_Brown_scLLC_2.5w_nps <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_2.5w_nps, slot.name = "netP")

cellchat_Brown_scLLC_2.5w_ccc <- computeCommunProb(cellchat_Brown_scLLC_2.5w_ccc)
cellchat_Brown_scLLC_2.5w_ccc <- computeCommunProbPathway(cellchat_Brown_scLLC_2.5w_ccc)
cellchat_Brown_scLLC_2.5w_ccc <- aggregateNet(cellchat_Brown_scLLC_2.5w_ccc)
cellchat_Brown_scLLC_2.5w_ccc <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_2.5w_ccc, slot.name = "netP")

# Brown_scLLC_3.5w
cellchat_Brown_scLLC_3.5w_all <- computeCommunProb(cellchat_Brown_scLLC_3.5w_all)
cellchat_Brown_scLLC_3.5w_all <- computeCommunProbPathway(cellchat_Brown_scLLC_3.5w_all)
cellchat_Brown_scLLC_3.5w_all <- aggregateNet(cellchat_Brown_scLLC_3.5w_all)
cellchat_Brown_scLLC_3.5w_all <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_3.5w_all, slot.name = "netP")

cellchat_Brown_scLLC_3.5w_secreted <- computeCommunProb(cellchat_Brown_scLLC_3.5w_secreted)
cellchat_Brown_scLLC_3.5w_secreted <- computeCommunProbPathway(cellchat_Brown_scLLC_3.5w_secreted)
cellchat_Brown_scLLC_3.5w_secreted <- aggregateNet(cellchat_Brown_scLLC_3.5w_secreted)
cellchat_Brown_scLLC_3.5w_secreted <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_3.5w_secreted, slot.name = "netP")

cellchat_Brown_scLLC_3.5w_ECM <- computeCommunProb(cellchat_Brown_scLLC_3.5w_ECM)
cellchat_Brown_scLLC_3.5w_ECM <- computeCommunProbPathway(cellchat_Brown_scLLC_3.5w_ECM)
cellchat_Brown_scLLC_3.5w_ECM <- aggregateNet(cellchat_Brown_scLLC_3.5w_ECM)
cellchat_Brown_scLLC_3.5w_ECM <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_3.5w_ECM, slot.name = "netP")

cellchat_Brown_scLLC_3.5w_nps <- computeCommunProb(cellchat_Brown_scLLC_3.5w_nps)
cellchat_Brown_scLLC_3.5w_nps <- computeCommunProbPathway(cellchat_Brown_scLLC_3.5w_nps)
cellchat_Brown_scLLC_3.5w_nps <- aggregateNet(cellchat_Brown_scLLC_3.5w_nps)
cellchat_Brown_scLLC_3.5w_nps <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_3.5w_nps, slot.name = "netP")

cellchat_Brown_scLLC_3.5w_ccc <- computeCommunProb(cellchat_Brown_scLLC_3.5w_ccc)
cellchat_Brown_scLLC_3.5w_ccc <- computeCommunProbPathway(cellchat_Brown_scLLC_3.5w_ccc)
cellchat_Brown_scLLC_3.5w_ccc <- aggregateNet(cellchat_Brown_scLLC_3.5w_ccc)
cellchat_Brown_scLLC_3.5w_ccc <- netAnalysis_computeCentrality(cellchat_Brown_scLLC_3.5w_ccc, slot.name = "netP")

# Kim_scB16F10_CTL
cellchat_Kim_scB16F10_CTL_all <- computeCommunProb(cellchat_Kim_scB16F10_CTL_all)
cellchat_Kim_scB16F10_CTL_all <- computeCommunProbPathway(cellchat_Kim_scB16F10_CTL_all)
cellchat_Kim_scB16F10_CTL_all <- aggregateNet(cellchat_Kim_scB16F10_CTL_all)
cellchat_Kim_scB16F10_CTL_all <- netAnalysis_computeCentrality(cellchat_Kim_scB16F10_CTL_all, slot.name = "netP")

cellchat_Kim_scB16F10_CTL_secreted <- computeCommunProb(cellchat_Kim_scB16F10_CTL_secreted)
cellchat_Kim_scB16F10_CTL_secreted <- computeCommunProbPathway(cellchat_Kim_scB16F10_CTL_secreted)
cellchat_Kim_scB16F10_CTL_secreted <- aggregateNet(cellchat_Kim_scB16F10_CTL_secreted)
cellchat_Kim_scB16F10_CTL_secreted <- netAnalysis_computeCentrality(cellchat_Kim_scB16F10_CTL_secreted, slot.name = "netP")

cellchat_Kim_scB16F10_CTL_ECM <- computeCommunProb(cellchat_Kim_scB16F10_CTL_ECM)
cellchat_Kim_scB16F10_CTL_ECM <- computeCommunProbPathway(cellchat_Kim_scB16F10_CTL_ECM)
cellchat_Kim_scB16F10_CTL_ECM <- aggregateNet(cellchat_Kim_scB16F10_CTL_ECM)
cellchat_Kim_scB16F10_CTL_ECM <- netAnalysis_computeCentrality(cellchat_Kim_scB16F10_CTL_ECM, slot.name = "netP")

cellchat_Kim_scB16F10_CTL_nps <- computeCommunProb(cellchat_Kim_scB16F10_CTL_nps)
cellchat_Kim_scB16F10_CTL_nps <- computeCommunProbPathway(cellchat_Kim_scB16F10_CTL_nps)
cellchat_Kim_scB16F10_CTL_nps <- aggregateNet(cellchat_Kim_scB16F10_CTL_nps)
cellchat_Kim_scB16F10_CTL_nps <- netAnalysis_computeCentrality(cellchat_Kim_scB16F10_CTL_nps, slot.name = "netP")

cellchat_Kim_scB16F10_CTL_ccc <- computeCommunProb(cellchat_Kim_scB16F10_CTL_ccc)
cellchat_Kim_scB16F10_CTL_ccc <- computeCommunProbPathway(cellchat_Kim_scB16F10_CTL_ccc)
cellchat_Kim_scB16F10_CTL_ccc <- aggregateNet(cellchat_Kim_scB16F10_CTL_ccc)
cellchat_Kim_scB16F10_CTL_ccc <- netAnalysis_computeCentrality(cellchat_Kim_scB16F10_CTL_ccc, slot.name = "netP")

# Kim_scB16F10_B16F10
cellchat_Kim_scB16F10_B16F10_all <- computeCommunProb(cellchat_Kim_scB16F10_B16F10_all)
cellchat_Kim_scB16F10_B16F10_all <- computeCommunProbPathway(cellchat_Kim_scB16F10_B16F10_all)
cellchat_Kim_scB16F10_B16F10_all <- aggregateNet(cellchat_Kim_scB16F10_B16F10_all)
cellchat_Kim_scB16F10_B16F10_all <- netAnalysis_computeCentrality(cellchat_Kim_scB16F10_B16F10_all, slot.name = "netP")

cellchat_Kim_scB16F10_B16F10_secreted <- computeCommunProb(cellchat_Kim_scB16F10_B16F10_secreted)
cellchat_Kim_scB16F10_B16F10_secreted <- computeCommunProbPathway(cellchat_Kim_scB16F10_B16F10_secreted)
cellchat_Kim_scB16F10_B16F10_secreted <- aggregateNet(cellchat_Kim_scB16F10_B16F10_secreted)
cellchat_Kim_scB16F10_B16F10_secreted <- netAnalysis_computeCentrality(cellchat_Kim_scB16F10_B16F10_secreted, slot.name = "netP")

cellchat_Kim_scB16F10_B16F10_ECM <- computeCommunProb(cellchat_Kim_scB16F10_B16F10_ECM)
cellchat_Kim_scB16F10_B16F10_ECM <- computeCommunProbPathway(cellchat_Kim_scB16F10_B16F10_ECM)
cellchat_Kim_scB16F10_B16F10_ECM <- aggregateNet(cellchat_Kim_scB16F10_B16F10_ECM)
cellchat_Kim_scB16F10_B16F10_ECM <- netAnalysis_computeCentrality(cellchat_Kim_scB16F10_B16F10_ECM, slot.name = "netP")

cellchat_Kim_scB16F10_B16F10_nps <- computeCommunProb(cellchat_Kim_scB16F10_B16F10_nps)
cellchat_Kim_scB16F10_B16F10_nps <- computeCommunProbPathway(cellchat_Kim_scB16F10_B16F10_nps)
cellchat_Kim_scB16F10_B16F10_nps <- aggregateNet(cellchat_Kim_scB16F10_B16F10_nps)
cellchat_Kim_scB16F10_B16F10_nps <- netAnalysis_computeCentrality(cellchat_Kim_scB16F10_B16F10_nps, slot.name = "netP")

cellchat_Kim_scB16F10_B16F10_ccc <- computeCommunProb(cellchat_Kim_scB16F10_B16F10_ccc)
cellchat_Kim_scB16F10_B16F10_ccc <- computeCommunProbPathway(cellchat_Kim_scB16F10_B16F10_ccc)
cellchat_Kim_scB16F10_B16F10_ccc <- aggregateNet(cellchat_Kim_scB16F10_B16F10_ccc)
cellchat_Kim_scB16F10_B16F10_ccc <- netAnalysis_computeCentrality(cellchat_Kim_scB16F10_B16F10_ccc, slot.name = "netP")

# Pryce_scC26_CTL
cellchat_Pryce_scC26_CTL_all <- computeCommunProb(cellchat_Pryce_scC26_CTL_all)
cellchat_Pryce_scC26_CTL_all <- computeCommunProbPathway(cellchat_Pryce_scC26_CTL_all)
cellchat_Pryce_scC26_CTL_all <- aggregateNet(cellchat_Pryce_scC26_CTL_all)
cellchat_Pryce_scC26_CTL_all <- netAnalysis_computeCentrality(cellchat_Pryce_scC26_CTL_all, slot.name = "netP")

cellchat_Pryce_scC26_CTL_secreted <- computeCommunProb(cellchat_Pryce_scC26_CTL_secreted)
cellchat_Pryce_scC26_CTL_secreted <- computeCommunProbPathway(cellchat_Pryce_scC26_CTL_secreted)
cellchat_Pryce_scC26_CTL_secreted <- aggregateNet(cellchat_Pryce_scC26_CTL_secreted)
cellchat_Pryce_scC26_CTL_secreted <- netAnalysis_computeCentrality(cellchat_Pryce_scC26_CTL_secreted, slot.name = "netP")

cellchat_Pryce_scC26_CTL_ECM <- computeCommunProb(cellchat_Pryce_scC26_CTL_ECM)
cellchat_Pryce_scC26_CTL_ECM <- computeCommunProbPathway(cellchat_Pryce_scC26_CTL_ECM)
cellchat_Pryce_scC26_CTL_ECM <- aggregateNet(cellchat_Pryce_scC26_CTL_ECM)
cellchat_Pryce_scC26_CTL_ECM <- netAnalysis_computeCentrality(cellchat_Pryce_scC26_CTL_ECM, slot.name = "netP")

cellchat_Pryce_scC26_CTL_nps <- computeCommunProb(cellchat_Pryce_scC26_CTL_nps)
cellchat_Pryce_scC26_CTL_nps <- computeCommunProbPathway(cellchat_Pryce_scC26_CTL_nps)
cellchat_Pryce_scC26_CTL_nps <- aggregateNet(cellchat_Pryce_scC26_CTL_nps)
cellchat_Pryce_scC26_CTL_nps <- netAnalysis_computeCentrality(cellchat_Pryce_scC26_CTL_nps, slot.name = "netP")

cellchat_Pryce_scC26_CTL_ccc <- computeCommunProb(cellchat_Pryce_scC26_CTL_ccc)
cellchat_Pryce_scC26_CTL_ccc <- computeCommunProbPathway(cellchat_Pryce_scC26_CTL_ccc)
cellchat_Pryce_scC26_CTL_ccc <- aggregateNet(cellchat_Pryce_scC26_CTL_ccc)
cellchat_Pryce_scC26_CTL_ccc <- netAnalysis_computeCentrality(cellchat_Pryce_scC26_CTL_ccc, slot.name = "netP")

# Pryce_scC26_C26
cellchat_Pryce_scC26_C26_all <- computeCommunProb(cellchat_Pryce_scC26_C26_all)
cellchat_Pryce_scC26_C26_all <- computeCommunProbPathway(cellchat_Pryce_scC26_C26_all)
cellchat_Pryce_scC26_C26_all <- aggregateNet(cellchat_Pryce_scC26_C26_all)
cellchat_Pryce_scC26_C26_all <- netAnalysis_computeCentrality(cellchat_Pryce_scC26_C26_all, slot.name = "netP")

cellchat_Pryce_scC26_C26_secreted <- computeCommunProb(cellchat_Pryce_scC26_C26_secreted)
cellchat_Pryce_scC26_C26_secreted <- computeCommunProbPathway(cellchat_Pryce_scC26_C26_secreted)
cellchat_Pryce_scC26_C26_secreted <- aggregateNet(cellchat_Pryce_scC26_C26_secreted)
cellchat_Pryce_scC26_C26_secreted <- netAnalysis_computeCentrality(cellchat_Pryce_scC26_C26_secreted, slot.name = "netP")

cellchat_Pryce_scC26_C26_ECM <- computeCommunProb(cellchat_Pryce_scC26_C26_ECM)
cellchat_Pryce_scC26_C26_ECM <- computeCommunProbPathway(cellchat_Pryce_scC26_C26_ECM)
cellchat_Pryce_scC26_C26_ECM <- aggregateNet(cellchat_Pryce_scC26_C26_ECM)
cellchat_Pryce_scC26_C26_ECM <- netAnalysis_computeCentrality(cellchat_Pryce_scC26_C26_ECM, slot.name = "netP")

cellchat_Pryce_scC26_C26_nps <- computeCommunProb(cellchat_Pryce_scC26_C26_nps)
cellchat_Pryce_scC26_C26_nps <- computeCommunProbPathway(cellchat_Pryce_scC26_C26_nps)
cellchat_Pryce_scC26_C26_nps <- aggregateNet(cellchat_Pryce_scC26_C26_nps)
cellchat_Pryce_scC26_C26_nps <- netAnalysis_computeCentrality(cellchat_Pryce_scC26_C26_nps, slot.name = "netP")

cellchat_Pryce_scC26_C26_ccc <- computeCommunProb(cellchat_Pryce_scC26_C26_ccc)
cellchat_Pryce_scC26_C26_ccc <- computeCommunProbPathway(cellchat_Pryce_scC26_C26_ccc)
cellchat_Pryce_scC26_C26_ccc <- aggregateNet(cellchat_Pryce_scC26_C26_ccc)
cellchat_Pryce_scC26_C26_ccc <- netAnalysis_computeCentrality(cellchat_Pryce_scC26_C26_ccc, slot.name = "netP")

# Pryce_scKPP_CTL
cellchat_Pryce_scKPP_CTL_all <- computeCommunProb(cellchat_Pryce_scKPP_CTL_all)
cellchat_Pryce_scKPP_CTL_all <- computeCommunProbPathway(cellchat_Pryce_scKPP_CTL_all)
cellchat_Pryce_scKPP_CTL_all <- aggregateNet(cellchat_Pryce_scKPP_CTL_all)
cellchat_Pryce_scKPP_CTL_all <- netAnalysis_computeCentrality(cellchat_Pryce_scKPP_CTL_all, slot.name = "netP")

cellchat_Pryce_scKPP_CTL_secreted <- computeCommunProb(cellchat_Pryce_scKPP_CTL_secreted)
cellchat_Pryce_scKPP_CTL_secreted <- computeCommunProbPathway(cellchat_Pryce_scKPP_CTL_secreted)
cellchat_Pryce_scKPP_CTL_secreted <- aggregateNet(cellchat_Pryce_scKPP_CTL_secreted)
cellchat_Pryce_scKPP_CTL_secreted <- netAnalysis_computeCentrality(cellchat_Pryce_scKPP_CTL_secreted, slot.name = "netP")

cellchat_Pryce_scKPP_CTL_ECM <- computeCommunProb(cellchat_Pryce_scKPP_CTL_ECM)
cellchat_Pryce_scKPP_CTL_ECM <- computeCommunProbPathway(cellchat_Pryce_scKPP_CTL_ECM)
cellchat_Pryce_scKPP_CTL_ECM <- aggregateNet(cellchat_Pryce_scKPP_CTL_ECM)
cellchat_Pryce_scKPP_CTL_ECM <- netAnalysis_computeCentrality(cellchat_Pryce_scKPP_CTL_ECM, slot.name = "netP")

cellchat_Pryce_scKPP_CTL_nps <- computeCommunProb(cellchat_Pryce_scKPP_CTL_nps)
cellchat_Pryce_scKPP_CTL_nps <- computeCommunProbPathway(cellchat_Pryce_scKPP_CTL_nps)
cellchat_Pryce_scKPP_CTL_nps <- aggregateNet(cellchat_Pryce_scKPP_CTL_nps)
cellchat_Pryce_scKPP_CTL_nps <- netAnalysis_computeCentrality(cellchat_Pryce_scKPP_CTL_nps, slot.name = "netP")

cellchat_Pryce_scKPP_CTL_ccc <- computeCommunProb(cellchat_Pryce_scKPP_CTL_ccc)
cellchat_Pryce_scKPP_CTL_ccc <- computeCommunProbPathway(cellchat_Pryce_scKPP_CTL_ccc)
cellchat_Pryce_scKPP_CTL_ccc <- aggregateNet(cellchat_Pryce_scKPP_CTL_ccc)
cellchat_Pryce_scKPP_CTL_ccc <- netAnalysis_computeCentrality(cellchat_Pryce_scKPP_CTL_ccc, slot.name = "netP")

# Pryce_scKPP_KPP
cellchat_Pryce_scKPP_KPP_all <- computeCommunProb(cellchat_Pryce_scKPP_KPP_all)
cellchat_Pryce_scKPP_KPP_all <- computeCommunProbPathway(cellchat_Pryce_scKPP_KPP_all)
cellchat_Pryce_scKPP_KPP_all <- aggregateNet(cellchat_Pryce_scKPP_KPP_all)
cellchat_Pryce_scKPP_KPP_all <- netAnalysis_computeCentrality(cellchat_Pryce_scKPP_KPP_all, slot.name = "netP")

cellchat_Pryce_scKPP_KPP_secreted <- computeCommunProb(cellchat_Pryce_scKPP_KPP_secreted)
cellchat_Pryce_scKPP_KPP_secreted <- computeCommunProbPathway(cellchat_Pryce_scKPP_KPP_secreted)
cellchat_Pryce_scKPP_KPP_secreted <- aggregateNet(cellchat_Pryce_scKPP_KPP_secreted)
cellchat_Pryce_scKPP_KPP_secreted <- netAnalysis_computeCentrality(cellchat_Pryce_scKPP_KPP_secreted, slot.name = "netP")

cellchat_Pryce_scKPP_KPP_ECM <- computeCommunProb(cellchat_Pryce_scKPP_KPP_ECM)
cellchat_Pryce_scKPP_KPP_ECM <- computeCommunProbPathway(cellchat_Pryce_scKPP_KPP_ECM)
cellchat_Pryce_scKPP_KPP_ECM <- aggregateNet(cellchat_Pryce_scKPP_KPP_ECM)
cellchat_Pryce_scKPP_KPP_ECM <- netAnalysis_computeCentrality(cellchat_Pryce_scKPP_KPP_ECM, slot.name = "netP")

cellchat_Pryce_scKPP_KPP_nps <- computeCommunProb(cellchat_Pryce_scKPP_KPP_nps)
cellchat_Pryce_scKPP_KPP_nps <- computeCommunProbPathway(cellchat_Pryce_scKPP_KPP_nps)
cellchat_Pryce_scKPP_KPP_nps <- aggregateNet(cellchat_Pryce_scKPP_KPP_nps)
cellchat_Pryce_scKPP_KPP_nps <- netAnalysis_computeCentrality(cellchat_Pryce_scKPP_KPP_nps, slot.name = "netP")

cellchat_Pryce_scKPP_KPP_ccc <- computeCommunProb(cellchat_Pryce_scKPP_KPP_ccc)
cellchat_Pryce_scKPP_KPP_ccc <- computeCommunProbPathway(cellchat_Pryce_scKPP_KPP_ccc)
cellchat_Pryce_scKPP_KPP_ccc <- aggregateNet(cellchat_Pryce_scKPP_KPP_ccc)
cellchat_Pryce_scKPP_KPP_ccc <- netAnalysis_computeCentrality(cellchat_Pryce_scKPP_KPP_ccc, slot.name = "netP")

# Zhang_snKIC_CTL
cellchat_Zhang_snKIC_CTL_all <- computeCommunProb(cellchat_Zhang_snKIC_CTL_all)
cellchat_Zhang_snKIC_CTL_all <- computeCommunProbPathway(cellchat_Zhang_snKIC_CTL_all)
cellchat_Zhang_snKIC_CTL_all <- aggregateNet(cellchat_Zhang_snKIC_CTL_all)
cellchat_Zhang_snKIC_CTL_all <- netAnalysis_computeCentrality(cellchat_Zhang_snKIC_CTL_all, slot.name = "netP")

cellchat_Zhang_snKIC_CTL_secreted <- computeCommunProb(cellchat_Zhang_snKIC_CTL_secreted)
cellchat_Zhang_snKIC_CTL_secreted <- computeCommunProbPathway(cellchat_Zhang_snKIC_CTL_secreted)
cellchat_Zhang_snKIC_CTL_secreted <- aggregateNet(cellchat_Zhang_snKIC_CTL_secreted)
cellchat_Zhang_snKIC_CTL_secreted <- netAnalysis_computeCentrality(cellchat_Zhang_snKIC_CTL_secreted, slot.name = "netP")

cellchat_Zhang_snKIC_CTL_ECM <- computeCommunProb(cellchat_Zhang_snKIC_CTL_ECM)
cellchat_Zhang_snKIC_CTL_ECM <- computeCommunProbPathway(cellchat_Zhang_snKIC_CTL_ECM)
cellchat_Zhang_snKIC_CTL_ECM <- aggregateNet(cellchat_Zhang_snKIC_CTL_ECM)
cellchat_Zhang_snKIC_CTL_ECM <- netAnalysis_computeCentrality(cellchat_Zhang_snKIC_CTL_ECM, slot.name = "netP")

cellchat_Zhang_snKIC_CTL_nps <- computeCommunProb(cellchat_Zhang_snKIC_CTL_nps)
cellchat_Zhang_snKIC_CTL_nps <- computeCommunProbPathway(cellchat_Zhang_snKIC_CTL_nps)
cellchat_Zhang_snKIC_CTL_nps <- aggregateNet(cellchat_Zhang_snKIC_CTL_nps)
cellchat_Zhang_snKIC_CTL_nps <- netAnalysis_computeCentrality(cellchat_Zhang_snKIC_CTL_nps, slot.name = "netP")

cellchat_Zhang_snKIC_CTL_ccc <- computeCommunProb(cellchat_Zhang_snKIC_CTL_ccc)
cellchat_Zhang_snKIC_CTL_ccc <- computeCommunProbPathway(cellchat_Zhang_snKIC_CTL_ccc)
cellchat_Zhang_snKIC_CTL_ccc <- aggregateNet(cellchat_Zhang_snKIC_CTL_ccc)
cellchat_Zhang_snKIC_CTL_ccc <- netAnalysis_computeCentrality(cellchat_Zhang_snKIC_CTL_ccc, slot.name = "netP")

# Zhang_snKIC_KIC
cellchat_Zhang_snKIC_KIC_all <- computeCommunProb(cellchat_Zhang_snKIC_KIC_all)
cellchat_Zhang_snKIC_KIC_all <- computeCommunProbPathway(cellchat_Zhang_snKIC_KIC_all)
cellchat_Zhang_snKIC_KIC_all <- aggregateNet(cellchat_Zhang_snKIC_KIC_all)
cellchat_Zhang_snKIC_KIC_all <- netAnalysis_computeCentrality(cellchat_Zhang_snKIC_KIC_all, slot.name = "netP")

cellchat_Zhang_snKIC_KIC_secreted <- computeCommunProb(cellchat_Zhang_snKIC_KIC_secreted)
cellchat_Zhang_snKIC_KIC_secreted <- computeCommunProbPathway(cellchat_Zhang_snKIC_KIC_secreted)
cellchat_Zhang_snKIC_KIC_secreted <- aggregateNet(cellchat_Zhang_snKIC_KIC_secreted)
cellchat_Zhang_snKIC_KIC_secreted <- netAnalysis_computeCentrality(cellchat_Zhang_snKIC_KIC_secreted, slot.name = "netP")

cellchat_Zhang_snKIC_KIC_ECM <- computeCommunProb(cellchat_Zhang_snKIC_KIC_ECM)
cellchat_Zhang_snKIC_KIC_ECM <- computeCommunProbPathway(cellchat_Zhang_snKIC_KIC_ECM)
cellchat_Zhang_snKIC_KIC_ECM <- aggregateNet(cellchat_Zhang_snKIC_KIC_ECM)
cellchat_Zhang_snKIC_KIC_ECM <- netAnalysis_computeCentrality(cellchat_Zhang_snKIC_KIC_ECM, slot.name = "netP")

cellchat_Zhang_snKIC_KIC_nps <- computeCommunProb(cellchat_Zhang_snKIC_KIC_nps)
cellchat_Zhang_snKIC_KIC_nps <- computeCommunProbPathway(cellchat_Zhang_snKIC_KIC_nps)
cellchat_Zhang_snKIC_KIC_nps <- aggregateNet(cellchat_Zhang_snKIC_KIC_nps)
cellchat_Zhang_snKIC_KIC_nps <- netAnalysis_computeCentrality(cellchat_Zhang_snKIC_KIC_nps, slot.name = "netP")

cellchat_Zhang_snKIC_KIC_ccc <- computeCommunProb(cellchat_Zhang_snKIC_KIC_ccc)
cellchat_Zhang_snKIC_KIC_ccc <- computeCommunProbPathway(cellchat_Zhang_snKIC_KIC_ccc)
cellchat_Zhang_snKIC_KIC_ccc <- aggregateNet(cellchat_Zhang_snKIC_KIC_ccc)
cellchat_Zhang_snKIC_KIC_ccc <- netAnalysis_computeCentrality(cellchat_Zhang_snKIC_KIC_ccc, slot.name = "netP")
```



# Remove unused objects from the environment

```{r}
rm(Agca_snLLC_CTL, Agca_snLLC_LLC, Brown_scLLC_CTL, Brown_scLLC_2w, Brown_scLLC_2.5w, Brown_scLLC_3.5w, Kim_scB16F10_CTL, Kim_scB16F10_B16F10, Pryce_scC26_CTL, Pryce_scC26_C26, Pryce_scKPP_CTL, Pryce_scKPP_KPP, Zhang_snKIC_CTL, Zhang_snKIC_KIC, samples_Agca_snLLC_CTL, data_input_Agca_snLLC_CTL, data_input_Agca_snLLC_LLC, data_input_Brown_scLLC_CTL, data_input_Brown_scLLC_2w, data_input_Brown_scLLC_2.5w, data_input_Brown_scLLC_3.5w, data_input_Kim_scB16F10_CTL, data_input_Kim_scB16F10_B16F10, data_input_Pryce_scC26_CTL, data_input_Pryce_scC26_C26, data_input_Pryce_scKPP_CTL, data_input_Pryce_scKPP_KPP, data_input_Zhang_snKIC_CTL, data_input_Zhang_snKIC_KIC, samples_Agca_snLLC_LLC, samples_Brown_scLLC_CTL, samples_Brown_scLLC_2w, samples_Brown_scLLC_2.5w, samples_Brown_scLLC_3.5w, samples_Kim_scB16F10_CTL, samples_Kim_scB16F10_B16F10, samples_Pryce_scC26_CTL, samples_Pryce_scC26_C26, samples_Pryce_scKPP_CTL, samples_Pryce_scKPP_KPP, samples_Zhang_snKIC_CTL, samples_Zhang_snKIC_KIC, labels_Agca_snLLC_CTL, labels_Agca_snLLC_LLC, labels_Brown_scLLC_CTL, labels_Brown_scLLC_2w, labels_Brown_scLLC_2.5w, labels_Brown_scLLC_3.5w, labels_Kim_scB16F10_CTL, labels_Kim_scB16F10_B16F10, labels_Pryce_scC26_CTL, labels_Pryce_scC26_C26, labels_Pryce_scKPP_CTL, labels_Pryce_scKPP_KPP, labels_Zhang_snKIC_CTL, labels_Zhang_snKIC_KIC, CellChatDB_ccc, CellChatDB_ECM, CellChatDB_nps, CellChatDB_secreted, cellchat_Agca_snLLC_CTL_meta, cellchat_Agca_snLLC_LLC_meta, cellchat_Brown_scLLC_CTL_meta, cellchat_Brown_scLLC_2w_meta, cellchat_Brown_scLLC_2.5w_meta, cellchat_Brown_scLLC_3.5w_meta, cellchat_Kim_scB16F10_CTL_meta, cellchat_Kim_scB16F10_B16F10_meta, cellchat_Pryce_scC26_CTL_meta, cellchat_Pryce_scC26_C26_meta, cellchat_Pryce_scKPP_CTL_meta, cellchat_Pryce_scKPP_KPP_meta, cellchat_Zhang_snKIC_CTL_meta, cellchat_Zhang_snKIC_KIC_meta)

rm(enrichedLR_Agca_snLLC_CTL_all, enrichedLR_Agca_snLLC_CTL_secreted, enrichedLR_Agca_snLLC_CTL_ECM, enrichedLR_Agca_snLLC_CTL_ccc, enrichedLR_Agca_snLLC_CTL_nps, enrichedLR_Agca_snLLC_LLC_all, enrichedLR_Agca_snLLC_LLC_secreted, enrichedLR_Agca_snLLC_LLC_ECM, enrichedLR_Agca_snLLC_LLC_ccc, enrichedLR_Agca_snLLC_LLC_nps, enrichedLR_Brown_scLLC_CTL_all, enrichedLR_Brown_scLLC_CTL_secreted, enrichedLR_Brown_scLLC_CTL_ECM, enrichedLR_Brown_scLLC_CTL_ccc, enrichedLR_Brown_scLLC_CTL_nps, enrichedLR_Brown_scLLC_2w_all, enrichedLR_Brown_scLLC_2w_secreted, enrichedLR_Brown_scLLC_2w_ECM, enrichedLR_Brown_scLLC_2w_ccc, enrichedLR_Brown_scLLC_2w_nps, enrichedLR_Brown_scLLC_2.5w_all, enrichedLR_Brown_scLLC_2.5w_secreted, enrichedLR_Brown_scLLC_2.5w_ECM, enrichedLR_Brown_scLLC_2.5w_ccc, enrichedLR_Brown_scLLC_2.5w_nps, enrichedLR_Brown_scLLC_3.5w_all, enrichedLR_Brown_scLLC_3.5w_secreted, enrichedLR_Brown_scLLC_3.5w_ECM, enrichedLR_Brown_scLLC_3.5w_ccc, enrichedLR_Brown_scLLC_3.5w_nps, enrichedLR_Kim_scB16F10_CTL_all, enrichedLR_Kim_scB16F10_CTL_secreted, enrichedLR_Kim_scB16F10_CTL_ECM, enrichedLR_Kim_scB16F10_CTL_ccc, enrichedLR_Kim_scB16F10_CTL_nps, enrichedLR_Kim_scB16F10_B16F10_all, enrichedLR_Kim_scB16F10_B16F10_secreted, enrichedLR_Kim_scB16F10_B16F10_ECM, enrichedLR_Kim_scB16F10_B16F10_ccc, enrichedLR_Kim_scB16F10_B16F10_nps, enrichedLR_Pryce_scC26_CTL_all, enrichedLR_Pryce_scC26_CTL_secreted, enrichedLR_Pryce_scC26_CTL_ECM, enrichedLR_Pryce_scC26_CTL_ccc, enrichedLR_Pryce_scC26_CTL_nps, enrichedLR_Pryce_scC26_C26_all, enrichedLR_Pryce_scC26_C26_secreted, enrichedLR_Pryce_scC26_C26_ECM, enrichedLR_Pryce_scC26_C26_ccc, enrichedLR_Pryce_scC26_C26_nps, enrichedLR_Pryce_scKPP_CTL_all, enrichedLR_Pryce_scKPP_CTL_secreted, enrichedLR_Pryce_scKPP_CTL_ECM, enrichedLR_Pryce_scKPP_CTL_ccc, enrichedLR_Pryce_scKPP_CTL_nps, enrichedLR_Pryce_scKPP_KPP_all, enrichedLR_Pryce_scKPP_KPP_secreted, enrichedLR_Pryce_scKPP_KPP_ECM, enrichedLR_Pryce_scKPP_KPP_ccc, enrichedLR_Pryce_scKPP_KPP_nps, enrichedLR_Zhang_snKIC_CTL_all, enrichedLR_Zhang_snKIC_CTL_secreted, enrichedLR_Zhang_snKIC_CTL_ECM, enrichedLR_Zhang_snKIC_CTL_ccc, enrichedLR_Zhang_snKIC_CTL_nps, enrichedLR_Zhang_snKIC_KIC_all, enrichedLR_Zhang_snKIC_KIC_secreted, enrichedLR_Zhang_snKIC_KIC_ECM, enrichedLR_Zhang_snKIC_KIC_ccc, enrichedLR_Zhang_snKIC_KIC_nps)

rm(enriched_pathways_Agca_snLLC_CTL_all, enriched_pathways_Agca_snLLC_CTL_secreted, enriched_pathways_Agca_snLLC_CTL_ECM, enriched_pathways_Agca_snLLC_CTL_ccc, enriched_pathways_Agca_snLLC_CTL_nps, enriched_pathways_Agca_snLLC_LLC_all, enriched_pathways_Agca_snLLC_LLC_secreted, enriched_pathways_Agca_snLLC_LLC_ECM, enriched_pathways_Agca_snLLC_LLC_ccc, enriched_pathways_Agca_snLLC_LLC_nps, enriched_pathways_Brown_scLLC_CTL_all, enriched_pathways_Brown_scLLC_CTL_secreted, enriched_pathways_Brown_scLLC_CTL_ECM, enriched_pathways_Brown_scLLC_CTL_ccc, enriched_pathways_Brown_scLLC_CTL_nps, enriched_pathways_Brown_scLLC_2w_all, enriched_pathways_Brown_scLLC_2w_secreted, enriched_pathways_Brown_scLLC_2w_ECM, enriched_pathways_Brown_scLLC_2w_ccc, enriched_pathways_Brown_scLLC_2w_nps, enriched_pathways_Brown_scLLC_2.5w_all, enriched_pathways_Brown_scLLC_2.5w_secreted, enriched_pathways_Brown_scLLC_2.5w_ECM, enriched_pathways_Brown_scLLC_2.5w_ccc, enriched_pathways_Brown_scLLC_2.5w_nps, enriched_pathways_Brown_scLLC_3.5w_all, enriched_pathways_Brown_scLLC_3.5w_secreted, enriched_pathways_Brown_scLLC_3.5w_ECM, enriched_pathways_Brown_scLLC_3.5w_ccc, enriched_pathways_Brown_scLLC_3.5w_nps, enriched_pathways_Kim_scB16F10_CTL_all, enriched_pathways_Kim_scB16F10_CTL_secreted, enriched_pathways_Kim_scB16F10_CTL_ECM, enriched_pathways_Kim_scB16F10_CTL_ccc, enriched_pathways_Kim_scB16F10_CTL_nps, enriched_pathways_Kim_scB16F10_B16F10_all, enriched_pathways_Kim_scB16F10_B16F10_secreted, enriched_pathways_Kim_scB16F10_B16F)
```



# THIS IS WHERE integrated_cellchat.Rdata ENDS!


# Load (above) data

```{r, include=FALSE}
load("C:/Users/nwb_l/Documents/r_projects/scIntegration/sc_combined_cellchat.RData")
```



# Enriched pathways

## List of enriched pathways per sample

### I want the option to select for every combination of samples/interaction types. For example, select experiment (Brown_scLLC) then sample (CTL) then interaction type (ECM).

```{r}
cellchat_#sample_#interaction_type@netP[["pathways]]

# List of samples: Agca_snLLC_CTL, Agca_snLLC_LLC, Brown_scLLC_CTL, Brown_scLLC_2w, Brown_scLLC_2.5w, Brown_scLLC_3.5w, Kim_scB16F10_CTL, Kim_scB16F10_B16F10, Pryce_scC26_CTL, Pryce_scC26_C26, Pryce_scKPP_CTL, Pryce_scKPP_KPP, Zhang_snKIC_CTL, Zhang_snKIC_KIC


# List of interaction types: all, secreted, ECM, ccc, nps


cellchat_Agca_snLLC_CTL_all@netP[["pathways"]]
cellchat_Agca_snLLC_CTL_secreted@netP[["pathways"]]
cellchat_Agca_snLLC_CTL_ECM@netP[["pathways"]]
cellchat_Agca_snLLC_CTL_nps@netP[["pathways"]]
cellchat_Agca_snLLC_CTL_ccc@netP[["pathways"]]

cellchat_Agca_snLLC_LLC_all@netP[["pathways"]]
cellchat_Agca_snLLC_LLC_secreted@netP[["pathways"]]
cellchat_Agca_snLLC_LLC_ECM@netP[["pathways"]]
cellchat_Agca_snLLC_LLC_nps@netP[["pathways"]]
cellchat_Agca_snLLC_LLC_ccc@netP[["pathways"]]

cellchat_Brown_scLLC_CTL_all@netP[["pathways"]]
cellchat_Brown_scLLC_CTL_secreted@netP[["pathways"]]
cellchat_Brown_scLLC_CTL_ECM@netP[["pathways"]]
cellchat_Brown_scLLC_CTL_nps@netP[["pathways"]]
cellchat_Brown_scLLC_CTL_ccc@netP[["pathways"]]

cellchat_Brown_scLLC_2w_all@netP[["pathways"]]
cellchat_Brown_scLLC_2w_secreted@netP[["pathways"]]
cellchat_Brown_scLLC_2w_ECM@netP[["pathways"]]
cellchat_Brown_scLLC_2w_nps@netP[["pathways"]]
cellchat_Brown_scLLC_2w_ccc@netP[["pathways"]]

cellchat_Brown_scLLC_2.5w_all@netP[["pathways"]]
cellchat_Brown_scLLC_2.5w_secreted@netP[["pathways"]]
cellchat_Brown_scLLC_2.5w_ECM@netP[["pathways"]]
cellchat_Brown_scLLC_2.5w_nps@netP[["pathways"]]
cellchat_Brown_scLLC_2.5w_ccc@netP[["pathways"]]

cellchat_Brown_scLLC_3.5w_all@netP[["pathways"]]
cellchat_Brown_scLLC_3.5w_secreted@netP[["pathways"]]
cellchat_Brown_scLLC_3.5w_ECM@netP[["pathways"]]
cellchat_Brown_scLLC_3.5w_nps@netP[["pathways"]]
cellchat_Brown_scLLC_3.5w_ccc@netP[["pathways"]]

cellchat_Kim_scB16F10_CTL_all@netP[["pathways"]]
cellchat_Kim_scB16F10_CTL_secreted@netP[["pathways"]]
cellchat_Kim_scB16F10_CTL_ECM@netP[["pathways"]]
cellchat_Kim_scB16F10_CTL_nps@netP[["pathways"]]
cellchat_Kim_scB16F10_CTL_ccc@netP[["pathways"]]

cellchat_Kim_scB16F10_B16F10_all@netP[["pathways"]]
cellchat_Kim_scB16F10_B16F10_secreted@netP[["pathways"]]
cellchat_Kim_scB16F10_B16F10_ECM@netP[["pathways"]]
cellchat_Kim_scB16F10_B16F10_nps@netP[["pathways"]]
cellchat_Kim_scB16F10_B16F10_ccc@netP[["pathways"]]

cellchat_Pryce_scC26_CTL_all@netP[["pathways"]]
cellchat_Pryce_scC26_CTL_secreted@netP[["pathways"]]
cellchat_Pryce_scC26_CTL_ECM@netP[["pathways"]]
cellchat_Pryce_scC26_CTL_nps@netP[["pathways"]]
cellchat_Pryce_scC26_CTL_ccc@netP[["pathways"]]

cellchat_Pryce_scC26_C26_all@netP[["pathways"]]
cellchat_Pryce_scC26_C26_secreted@netP[["pathways"]]
cellchat_Pryce_scC26_C26_ECM@netP[["pathways"]]
cellchat_Pryce_scC26_C26_nps@netP[["pathways"]]
cellchat_Pryce_scC26_C26_ccc@netP[["pathways"]]

cellchat_Pryce_scKPP_CTL_all@netP[["pathways"]]
cellchat_Pryce_scKPP_CTL_secreted@netP[["pathways"]]
cellchat_Pryce_scKPP_CTL_ECM@netP[["pathways"]]
cellchat_Pryce_scKPP_CTL_nps@netP[["pathways"]]
cellchat_Pryce_scKPP_CTL_ccc@netP[["pathways"]]

cellchat_Pryce_scKPP_KPP_all@netP[["pathways"]]
cellchat_Pryce_scKPP_KPP_secreted@netP[["pathways"]]
cellchat_Pryce_scKPP_KPP_ECM@netP[["pathways"]]
cellchat_Pryce_scKPP_KPP_nps@netP[["pathways"]]
cellchat_Pryce_scKPP_KPP_ccc@netP[["pathways"]]

cellchat_Zhang_snKIC_CTL_all@netP[["pathways"]]
cellchat_Zhang_snKIC_CTL_secreted@netP[["pathways"]]
cellchat_Zhang_snKIC_CTL_ECM@netP[["pathways"]]
cellchat_Zhang_snKIC_CTL_nps@netP[["pathways"]]
cellchat_Zhang_snKIC_CTL_ccc@netP[["pathways"]]

cellchat_Zhang_snKIC_KIC_all@netP[["pathways"]]
cellchat_Zhang_snKIC_KIC_secreted@netP[["pathways"]]
cellchat_Zhang_snKIC_KIC_ECM@netP[["pathways"]]
cellchat_Zhang_snKIC_KIC_nps@netP[["pathways"]]
cellchat_Zhang_snKIC_KIC_ccc@netP[["pathways"]]
```
### NOTE - have option to download as a csv file or text file!


## List of enriched ligand-receptor pairs per sample.

### I want the option to select for every combination of samples/interaction types. For example, select experiment (Brown_scLLC) then sample (CTL) then interaction type (ECM).

```{r}
extractEnrichedLR(cellchat_#sample_#interaction_type, signaling = c(cellchat_#sample_#interaction_type@netP[["pathways"]]), geneLR.return = TRUE)

# List of samples: Agca_snLLC_CTL, Agca_snLLC_LLC, Brown_scLLC_CTL, Brown_scLLC_2w, Brown_scLLC_2.5w, Brown_scLLC_3.5w, Kim_scB16F10_CTL, Kim_scB16F10_B16F10, Pryce_scC26_CTL, Pryce_scC26_C26, Pryce_scKPP_CTL, Pryce_scKPP_KPP, Zhang_snKIC_CTL, Zhang_snKIC_KIC


# List of interaction types: all, secreted, ECM, ccc, nps

extractEnrichedLR(cellchat_Agca_snLLC_CTL_all, signaling = c(cellchat_Agca_snLLC_CTL_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Agca_snLLC_CTL_secreted, signaling = c(cellchat_Agca_snLLC_CTL_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Agca_snLLC_CTL_ECM, signaling = c(cellchat_Agca_snLLC_CTL_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Agca_snLLC_CTL_nps, signaling = c(cellchat_Agca_snLLC_CTL_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Agca_snLLC_CTL_ccc, signaling = c(cellchat_Agca_snLLC_CTL_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Agca_snLLC_LLC_all, signaling = c(cellchat_Agca_snLLC_LLC_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Agca_snLLC_LLC_secreted, signaling = c(cellchat_Agca_snLLC_LLC_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Agca_snLLC_LLC_ECM, signaling = c(cellchat_Agca_snLLC_LLC_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Agca_snLLC_LLC_nps, signaling = c(cellchat_Agca_snLLC_LLC_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Agca_snLLC_LLC_ccc, signaling = c(cellchat_Agca_snLLC_LLC_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Brown_scLLC_CTL_all, signaling = c(cellchat_Brown_scLLC_CTL_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_CTL_secreted, signaling = c(cellchat_Brown_scLLC_CTL_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_CTL_ECM, signaling = c(cellchat_Brown_scLLC_CTL_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_CTL_nps, signaling = c(cellchat_Brown_scLLC_CTL_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_CTL_ccc, signaling = c(cellchat_Brown_scLLC_CTL_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Brown_scLLC_2w_all, signaling = c(cellchat_Brown_scLLC_2w_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_2w_secreted, signaling = c(cellchat_Brown_scLLC_2w_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_2w_ECM, signaling = c(cellchat_Brown_scLLC_2w_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_2w_nps, signaling = c(cellchat_Brown_scLLC_2w_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_2w_ccc, signaling = c(cellchat_Brown_scLLC_2w_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Brown_scLLC_2.5w_all, signaling = c(cellchat_Brown_scLLC_2.5w_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_2.5w_secreted, signaling = c(cellchat_Brown_scLLC_2.5w_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_2.5w_ECM, signaling = c(cellchat_Brown_scLLC_2.5w_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_2.5w_nps, signaling = c(cellchat_Brown_scLLC_2.5w_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_2.5w_ccc, signaling = c(cellchat_Brown_scLLC_2.5w_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Brown_scLLC_3.5w_all, signaling = c(cellchat_Brown_scLLC_3.5w_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_3.5w_secreted, signaling = c(cellchat_Brown_scLLC_3.5w_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_3.5w_ECM, signaling = c(cellchat_Brown_scLLC_3.5w_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_3.5w_nps, signaling = c(cellchat_Brown_scLLC_3.5w_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Brown_scLLC_3.5w_ccc, signaling = c(cellchat_Brown_scLLC_3.5w_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Kim_scB16F10_CTL_all, signaling = c(cellchat_Kim_scB16F10_CTL_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Kim_scB16F10_CTL_secreted, signaling = c(cellchat_Kim_scB16F10_CTL_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Kim_scB16F10_CTL_ECM, signaling = c(cellchat_Kim_scB16F10_CTL_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Kim_scB16F10_CTL_nps, signaling = c(cellchat_Kim_scB16F10_CTL_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Kim_scB16F10_CTL_ccc, signaling = c(cellchat_Kim_scB16F10_CTL_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Kim_scB16F10_B16F10_all, signaling = c(cellchat_Kim_scB16F10_B16F10_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Kim_scB16F10_B16F10_secreted, signaling = c(cellchat_Kim_scB16F10_B16F10_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Kim_scB16F10_B16F10_ECM, signaling = c(cellchat_Kim_scB16F10_B16F10_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Kim_scB16F10_B16F10_nps, signaling = c(cellchat_Kim_scB16F10_B16F10_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Kim_scB16F10_B16F10_ccc, signaling = c(cellchat_Kim_scB16F10_B16F10_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Pryce_scC26_CTL_all, signaling = c(cellchat_Pryce_scC26_CTL_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scC26_CTL_secreted, signaling = c(cellchat_Pryce_scC26_CTL_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scC26_CTL_ECM, signaling = c(cellchat_Pryce_scC26_CTL_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scC26_CTL_nps, signaling = c(cellchat_Pryce_scC26_CTL_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scC26_CTL_ccc, signaling = c(cellchat_Pryce_scC26_CTL_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Pryce_scC26_C26_all, signaling = c(cellchat_Pryce_scC26_C26_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scC26_C26_secreted, signaling = c(cellchat_Pryce_scC26_C26_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scC26_C26_ECM, signaling = c(cellchat_Pryce_scC26_C26_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scC26_C26_nps, signaling = c(cellchat_Pryce_scC26_C26_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scC26_C26_ccc, signaling = c(cellchat_Pryce_scC26_C26_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Pryce_scKPP_CTL_all, signaling = c(cellchat_Pryce_scKPP_CTL_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scKPP_CTL_secreted, signaling = c(cellchat_Pryce_scKPP_CTL_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scKPP_CTL_ECM, signaling = c(cellchat_Pryce_scKPP_CTL_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scKPP_CTL_nps, signaling = c(cellchat_Pryce_scKPP_CTL_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scKPP_CTL_ccc, signaling = c(cellchat_Pryce_scKPP_CTL_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Pryce_scKPP_KPP_all, signaling = c(cellchat_Pryce_scKPP_KPP_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scKPP_KPP_secreted, signaling = c(cellchat_Pryce_scKPP_KPP_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scKPP_KPP_ECM, signaling = c(cellchat_Pryce_scKPP_KPP_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scKPP_KPP_nps, signaling = c(cellchat_Pryce_scKPP_KPP_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Pryce_scKPP_KPP_ccc, signaling = c(cellchat_Pryce_scKPP_KPP_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Zhang_snKIC_CTL_all, signaling = c(cellchat_Zhang_snKIC_CTL_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Zhang_snKIC_CTL_secreted, signaling = c(cellchat_Zhang_snKIC_CTL_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Zhang_snKIC_CTL_ECM, signaling = c(cellchat_Zhang_snKIC_CTL_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Zhang_snKIC_CTL_nps, signaling = c(cellchat_Zhang_snKIC_CTL_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Zhang_snKIC_CTL_ccc, signaling = c(cellchat_Zhang_snKIC_CTL_ccc@netP[["pathways"]]), geneLR.return = TRUE)

extractEnrichedLR(cellchat_Zhang_snKIC_KIC_all, signaling = c(cellchat_Zhang_snKIC_KIC_all@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Zhang_snKIC_KIC_secreted, signaling = c(cellchat_Zhang_snKIC_KIC_secreted@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Zhang_snKIC_KIC_ECM, signaling = c(cellchat_Zhang_snKIC_KIC_ECM@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Zhang_snKIC_KIC_nps, signaling = c(cellchat_Zhang_snKIC_KIC_nps@netP[["pathways"]]), geneLR.return = TRUE)
extractEnrichedLR(cellchat_Zhang_snKIC_KIC_ccc, signaling = c(cellchat_Zhang_snKIC_KIC_ccc@netP[["pathways"]]), geneLR.return = TRUE)
```
### NOTE - have option to download as a csv file or text file!


## Identify enriched pathways from one cell type (or group of cells) to another

```{r}
### Extract communication probabilities at the pathway level
netP_subset <- subsetCommunication(#cellchat_orig.ident_interaction.type, slot.name = "netP")

### Subset for enriched pathways for target cells to source cells
netP_subset <- netP_subset[
  netP_subset$source %in% c("#source_cell_1", "#source_cell_2", "#etc.") & 
  netP_subset$target %in% c("#target_cell_1", "#target_cell_2", "#etc."), 
]

### Get unique pathways from specified cells to target cells
pathways_subset <- unique(netP_subset$pathway_name)


head(pathways_subset)
```
### NOTE - have option to download as a csv file or text file!


# Visualize

## Specify colours (specify here, if not leave blank and will use default colours)

```{r, include=FALSE}
cluster_colours <- c(
  "Satellite cells" = "",
  "Myoblasts" = "",
  "Myonuclei" = "",
  "Endothelial cells" = "",
  "vSMCs" = "",
  "Pericytes" = "",
  "FAPs" = "",
  "Tenocytes" = "",
  "Platelets" = "",
  "Mast cells" = "",
  "Dendritic cells" = "",
  "Monocytes/macrophages" = "",
  "Neutrophils" = "",
  "B cells" = "",
  "T cells" = "",
  "NK cells" = "",
  "Neural/glial cells" = "",
  "Schwann cells" = ""
)
```


## Heatmap, interaction strength between all cell types

```{r}
netVisual_heatmap(#cellchat_orig.ident_interaction.type, 
  slot.name = "net", 
  measure = "weight", 
  color.heatmap = "Reds", 
  color.use = cluster_colours   # Ignore if not specified
  )
```


## Heatmap, contribution of each cell type to enriched signaling pathways

```{r}
netAnalysis_signalingRole_heatmap(
  #cellchat_orig.ident_interaction.type,
  pattern = "all",          # specify "all", "incoming", "outgoing"
  slot.name = "netP",
  color.heatmap = "Reds",
  color.use = cluster_colours, 
  width = 20,
  height = 20,
  font.size = 3
)
```


## Circle plots

```{r}
netVisual_circle(#cellchat_orig.ident_interaction.type@net$count, 
                 weight.scale = TRUE, 
                 label.edge = TRUE, # Can specify FALSE to remove numbers
                 title.name = "Number of interactions", 
                 arrow.size = 0.05,
                 color.use = cluster_colours, 
                 sources.use = c("#source_cell_1", "#source_cell_2", "#etc."), # Specify cell types SENDING signals or leave blank for all
                 targets.use = c("#target_cell_1", "#target_cell_2", "#etc.")) # Specify cell types RECIEVING signals or leave blank for all
```


## Chord plots

```{r}
par(mfrow = c(1, 1), xpd = TRUE)
par(cex = 0.5)

netVisual_chord_gene(#cellchat_orig.ident_interaction.type, 
  signaling = "#signaling pathway", 
  sources.use = c("#source_cell_1", "#source_cell_2", "#etc."),
  targets.use = c("#target_cell_1", "#target_cell_2", "#etc."), 
  color.use = cluster_colours, 
  show.legend = TRUE)
```
